%
% !TeX root = Gilligan_CV.tex
%
\subsubsection{Tenure-Track}
\emph{The following were published on tenure-track}

\begin{enumerate}
    \item 
    K. Best*, \textbf{J.M. Gilligan}, K.G. Rogers, A. Carrico, K. Donato, B. Ackerly, and B. Mallick,
    \enquote{A Machine Learning Analysis of Multiple Social Surveys to Understand Environmental Migration in Coastal Bangladesh},
    Amer.\ Geophys.\ Union Fall Meeting 2018

    \item 
    A. Witte*, G.M. Hornberger, T. Gunda, and \textbf{J.M. Gilligan},
    \enquote{A Study of the Geographic Variances in Water Salience using Local Newspapers},
    Amer.\ Geophys.\ Union Fall Meeting 2018
    
    \item 
    L.A. Valentine*,  C. Wilson, K.G. Rogers, A. Carrico, K. Donato, and \textbf{J.M. Gilligan},
    \enquote{Sediment Accretion and Erosion in Poldered and Non-Poldered Regions within the 
        Ganges-Brahmaputra-Meghna Delta, Bangladesh: Implications for River Channel Migration and Flood Risk},
    Amer.\ Geophys.\ Union Fall Meeting 2018
    
    \item 
    K. Best*, \textbf{J.M. Gilligan}, H. Baroud, B. Ackerly, and B. Mallick,
    \enquote{Machine Learning to Identify Drivers of Internal Migration in Coastal Bangladesh},
    Community Surface Dynamics Modeling System Annual Meeting, 2018.
    
    \item 
    *C.M. Tasich, \textbf{J.M. Gilligan}, S.L. Goodbred Jr, R.P. Hale, and C. Wilson,
    \enquote{Modeling Elevation Equilibrium and Human Adaptation in the Ganges-Brahmaputra Delta},
    Amer.\ Geophys.\ Union Fall Meeting 2017
    
    \item 
    C. Tasich*, \textbf{J.M. Gilligan}, S. Goodbred, R. Hale, and C. Wilson,
    \enquote{Modeling Elevation Equilibrium and Human Adaptation in Southwest Bangladesh},
    Community Surface Dynamics Modeling System Annual Meeting, 2017.

    \item 
    E.K. Burchfield* and \textbf{J.M. Gilligan},
    \enquote{Dynamics of Individual and Collective Agricultural Adaptation to Water Scarcity},
    Amer.\ Geophys.\ Union Fall Meeting 2016
    
    \item 
    C. Tasich*, \textbf{J.M. Gilligan}, S.L. Goodbred, R.P. Hale, and C. Wilson,
    \enquote{Modeling Elevation Equilibrium in the Face of Sea Level Rise },
    Amer.\ Geophys.\ Union Fall Meeting 2016

    \item 
    A. Carrico, \textbf{J.M. Gilligan}, and H.B. Truelove,
    \enquote{Actual vs. Perceived Climate Variability among Smallholding Rice Farmers},
    Amer.\ Geophys.\ Union Fall Meeting 2016

    \item \textbf{J.M. Gilligan}, J.J. Nay*, and M. Van der Linden*,
    \enquote{Prediction Markets and Beliefs about Climate: Results from Agent-Based Simulations},
    Amer.\ Geophys.\ Union Fall Meeting 2015
    
    \item \textbf{J.M. Gilligan}, C. Brady, J.V. Camp, J.J. Nay*, and P. Sengupta,
    \enquote{Emotional Engagement with Participatory Simulations as a Tool for Learning and Decision-Support for Coupled Human-Natural Systems: Flood Hazards and Urban Development},
    Amer.\ Geophys.\ Union Fall Meeting 2015
    
    \item M.G. Patrick*, S.L. Goodbred, \textbf{J.M. Gilligan}, C.M. Tasich*, S. Hossain, and K.M. Ahmed
    \enquote{Stratigraphic Evolution of the Ganges-Brahmaputra Lower Delta Plain and its Relation to Groundwater Arsenic Distributions},
    Amer.\ Geophys.\ Union Fall Meeting 2015

    \item C.M. Tasich*, \textbf{J.M. Gilligan}, S.L. Goodbred, C. Wilson, R.P. Hale, and L.W. Auerbach
    \enquote{Rejuvenating Poldered Landscapes: A Numerical Model of Elevation Equilibrium in Coastal Bangladesh},
    Amer.\ Geophys.\ Union Fall Meeting 2015

    \item T. Gunda*, \textbf{J.M. Gilligan}, and G.M. Hornberger
    \enquote{Forecasts of Agricultural Drought in Sri Lanka},
    Amer.\ Geophys.\ Union Fall Meeting 2015  
\end{enumerate}

\subsubsection{Pre-Tenure Track}
\emph{The following were published pre-tenure-track}

\begin{enumerate}

    \item \textbf{J. Gilligan}, B. Ackerly, S. Goodbred, and C. Wilson
    \enquote{Land Use, Livelihoods, Vulnerabilities, and Resilience in Coastal Bangladesh,}
    Amer.\ Geophys.\ Union Fall Meeting 2014

    \item \textbf{J. Gilligan} and M. Vandenbergh,    
    \enquote{Between Too Little and Too Late: Political Opportunity Costs in Climate Policy Analysis,}
    Amer.\ Geophys.\ Union Fall Meeting 2014

    \item G.M. Hornberger, \textbf{J. Gilligan}, and D. Hess
    \enquote{Water Conservation and Hydrological Transitions in Cities,}
    Amer.\ Geophys.\ Union Fall Meeting 2014

    \item S. Goodbred, M. Steckler, \textbf{J. Gilligan}, B. Ackerly, J. Ayers, C. Wilson, C. Small, and L. Seeber
    \enquote{Dynamic Asia: Coupling of climate, tectonics, rivers, and people defines risk and opportunity for the world’s largest human populations,}
    Amer.\ Geophys.\ Union Fall Meeting 2014

    \item C. Tasich*, S. Goodbred, \textbf{J. Gilligan}, and C. Wilson,
    \enquote{Rejuvenating Poldered Landscapes in a Tidally-Dominated, Sediment-Rich Delta: A Numerical Model and Analysis of the Effectiveness of Tidal River Management in Coastal Bangladesh,}
    Amer.\ Geophys.\ Union Fall Meeting 2014
    
    \item M. Steckler, S. Goodbred, S. Lowes, \textbf{J. Gilligan}, B. Ackerly, K.M. Ahmed, S. Akhter, D. Sousa, C. Wilson, D. Datta, K. Roy, and D. Mondal*,
    \enquote{Enhancing University Courses and Field Schools through Cross-cultural Exchange: Joint US-Bangladeshi Trips to the Ganges-Brahmaputra and Mississippi Deltas,}
    Amer.\ Geophys.\ Union Fall Meeting 2014

    \item \textbf{J. Gilligan}, B. Ackerly, and S. Goodbred,
    \enquote{Integrating social science, environmental science, and engineering to understand vulnerability and resilience to environmental hazards in Bangladesh,}
    Amer.\ Geophys.\ Union Fall Meeting 2013.
    
    \item \textbf{J. Gilligan}, B. Ackerly, K. Ahmed, L. Auerbach*, L. Benneyworth*, S. Goodbred, J. Jacobi*,  D. Mondal*, J. Pickering*, K. Rogers, and K. Roy,
    \enquote{Water and social justice in Bangladesh: A transdisciplinary and intercultural approach,}
    Amer.\ Geophys.\ Union Fall Meeting 2013.
    
    \item L. Auerbach*, S. Goodbred, D. Mondal*, C. Wilson, K. Ahmed, K. Roy, M. Steckler, \textbf{J. Gilligan}, and S. Nooner
    \enquote{In the Balance: Natural v. Embanked Landscapes in the Ganges-Brahmaputra Tidal Delta Plain},
    Amer.\ Geophys.\ Union Fall Meeting 2013.
    
    \item S. Goodbred, L. Auerbach*, C. Wilson, \textbf{J. Gilligan}, K. Roy, K. Ahmed, M. Steckler, L. Seeber, S. Akhter, and S. Hossain*,
    \enquote{A Tale of Two Deltas: Contrasting Perspectives on the Status of Natural and Human-modified Regions of the Ganges-Brahmaputra River Delta,}
    Amer.\ Geophys.\ Union Fall Meeting 2013.
    
    \item \textbf{J. Gilligan},
    \enquote{Integrating social and natural science to understand vulnerability and resilience in coastal environments,}
    Coastal Processes and Environments Under Sea-Level Rise and Changing Climate: Science to Inform Management, Joint Penrose/Chapman Conference,
    Geol.\ Soc.\ Amer.\ \& Amer.\ Geophys.\ Soc., Galveston TX, 14-19 Apr.~2013.
    
    \item \textbf{J. Gilligan}, B. Ackerly, and S. Goodbred,
    \enquote{Building resilience to environmental stress in coastal Bangladesh: An integrated social, environmental, and engineering perspective,}
    Bridging the Policy-Action Divide: Challenges and Prospects for Bangladesh, Bangladesh Development Initiative, Berkeley CA, 22--24~Feb., 2013.

    \item J.H. Jacobi*, \textbf{J.M. Gilligan}, A.R. Carrico, H.B. Truelove, and G. Hornberger,
    \enquote{Diffusion of a Sustainable Farming Technique in Sri Lanka: An Agent-Based Modeling Approach,}
    Amer.\ Geophys.\ Union Fall Meeting 2012, abstract \#1479443.

    \item
    L. Auerbach*, S.L. Goodbred, D. Mondal*, K. Roy, K.R. Ahmed*, \textbf{J.M. Gilligan}, and B. Ackerly,
    \enquote{Contrasting Pristine and Human-Modified Deltaic Environments: Severe Consequences from Long-Term Coastal Embankments in Southwest Bangladesh,}
    Amer.\ Geophys.\ Union Fall Meeting 2012, abstract \#1496486.
  
    \item \textbf{J.M. Gilligan}, N.H. Tolk, A. Cricenti, R. Generosi, P. Perfetti, C. Coluzza, and G. Margaritondo, 
    \enquote{Infrared near-field spectromicroscopy of buried interfaces using free-electron lasers}, by
    Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p. 2607.

    \item \enquote{Infrared Wavelength Selective Modification of Doped Hydrogenated Silicon},
    by C. Parks Cheney*, G. L{\"u}pke, J.C. Keay, \textbf{J.M. Gilligan}, L.C. Feldman, N.H. Tolk, S. Chen, P.C. Taylor, Y. Tung, and D.O. Henderson, 
    Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p. 2302.

\item
  G. Mensing*, J.M. Gilligan, E. Hurt*, N. Tolk, and P.C. Taylor,
  \enquote{Photoluminescenc Excitation Spectroscopy of a-Si: H using a Free-Electron Laser},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p. 2704.

\item
  Z. Hargitai*, Y. Yao*, \textbf{J.M. Gilligan}, B. Pratt-Ferguson*, V.D. Gordon*, A. Puckett*, N.H. Tolk, J. Tully, G. Betz, and W. Husinsky,
  \enquote{Observation of Enhanced Sputtering by Molecular Ions at Near-Threshold Energies},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p.~2813.

\item
  W. Wang*, G. L{\"u}pke, \textbf{J.M. Gilligan}, L.C. Feldman, N.H. Tolk, G. Lucovsky, and I.C. Kiziyalli,
  \enquote{Wavelength-Selective Alteration of the Si (001)/SiO2 Interface by Intense Tunable Infrared Radiation},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p.~1510.

\item
  C. Parks Cheney*, G. L\"upke, J.C. Keay, \textbf{J.M. Gilligan}, L.C. Feldman, N.H. Tolk, S. Chen, P.C. Taylor, Y. Tung, and D.O. Henderson,
  \enquote{Infrared Wavelength Selective Modification of Doped Hydrogenated Silicon},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p.~2302.

\item
  \textbf{J.M. Gilligan}, N.H. Tolk, A. Cricenti, R. Generosi, P. Perfetti, C. Coluzza, and G. Margaritondo,
  \enquote{Infrared Near-Field Spectromicroscopy of Buried Interfaces using Free-Electron Lasers},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p.~2607.

\item
  Z. Hartigai*, Y. Yao*, \textbf{J.M. Gilligan}, B. Pratt-Ferguson*, V.D. Gordon*, A. Puckett*, N.H. Tolk, J. Tully, G. Betz, and W. Husinsky,
  \enquote{Observation of Enhanced Sputtering by Molecular Ions at Near-Threshold Energies},
Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1998, p.~2813.


\item
  Z. Hargitai*, Y. Yao*, M.M. Albert*, A.V. Barnes, \textbf{J.M. Gilligan}, V.D. Gordon*, G. L{\"u}pke, B. Pratt-Ferguson*, A. Puckett*, and N.H. Tolk,
  \enquote{Enhancement of Sputtering Yields by Low-Energy Molecular Ions},
  APS Southeastern Section Meeting Abstracts (1997), p.~9.

\item
  J. Sturmann*, R.G. Albridge, \textbf{J.M. Gilligan}, G. L\"upke, N.H. Tolk, and J.L. Davidson,
  \enquote{Infrared Wavelength-Selective Photodesorption from Diamond Films},
  APS Southeastern Section Meeting (1997), p.~8.

\item
  G. Mensing*, \textbf{J. Gilligan}, E. Hurt*, N.H. Tolk, and P.C. Taylor,
  \enquote{Photoluminescence Excitation Spectroscopy of a-si: H Using a Free Electron Laser},
Bull.\ Amer.\ Phys.\ Soc.\ March 1997, p.~1202.

\item
  G.S. Herold*, M.S. Salib*, A. Petrou, B.D. McCombe, G. Mensing*, \textbf{J. Gilligan}, N. Tolk, M. Dutta, J. Pamulapati, and P.G. Newman,
  \enquote{Optically Detected Resonance Spectroscopy of Intersubband Transitions in GaAs/AlAs Multiple Quantum Wells},
  APS Southeastern Section Meeting (1997), p.~4.

\item
  \textbf{J. Gilligan}, G. Mensing*, N. Tolk, M.S. Salib*, A. Petrou, B.D. McCombe, M. Dutta, J. Pamulapati, and P.G. Newman,
  \enquote{Free Electron Laser Optically Detected Resonance Spectroscopy of Intersubband Transitions in GaAs/AlAs Quantum Wells}, 
  Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1997, p. 1209.

\item
  G.A. Mensing*, E. Hurt*, \textbf{J. Gilligan}, N. Tolk, and P.C. Taylor,
  \enquote{Photoluminescence of a-Si: H using a Free Electron Laser},
  APS Southeastern Section Meeting (1996), p.~12.


\item
  M.T. Graham*, R.G. Albridge, A. Barnes, B. Barnes*, A. Beth, J. Davidson, \textbf{J. Gilligan}, J. McKinley, S. Pantelides, and N. Tolk, Bull.\ Amer.\ Phys.\ Soc.\ Mar.~1996, p.~2702.
  \enquote{Nonthermal Diffusion of Impurities in Silicon and Diamond},
  
 \item
 U. Eichmann, J.C. Bergquist, J.J. Bollinger, and \textbf{J.M. Gilligan},
 \enquote{Young`s interference experiment with light scattered from two atoms},
 Bull. Amer. Phys. Soc. \textbf{38}, May~1993, p.~1140 (1993).

\item
 \textbf{J.M. Gilligan}, C. Monroe, and D. Wineland,
  \enquote{A miniature linear RF ion trap},
  Bull. Amer. Phys. Soc., \textbf{38}, May~1993.
\end{enumerate}
