%
% !TeX root = jmg_cv.tex
%
\begin{rubric}{Professional Activities}%
\entry*[2015--]Collaboration with University School of Nashville teacher Wilson Hubbell to incorporate scientific literacy about mathematical and commputational modeling into high-school science curricula (Funding to USN from Edwin E. Ford Foundation).
\entry*[2007--]Associate director for Research, Vanderbilt Climate Change Research Network.
\entry*[2003--]Communication of Science and Technology Committee, Vanderbilt University.
\entry*[2015]Panelist, ``Grand Challenge: Energy and the Future,'' (Vanderbilt Board of Trust Meeting, 13~Feb.)
\entry*[2013]Panelist, ``Starting the Conversation: Inspiring Your Students to Write,'' Center for Teaching/Writing Studio/Heard Library, Vanderbilt University. Aug.~29.
\entry*[2012]Co-author, \textit{Sustainable Tennessee}, a report to state and local decision-makers on the impacts of climate change on Tennessee and possible adaptations. Oak Ridge National Laboratory.
\entry*[2009]Briefed representatives of Senators Corker and Alexander on environmental aspects of the UN Convention on the Law of the Sea.
% (Pew Charitable Trusts), 
Nov. 18.
\entry*[2008]Invited panelist, Public Policy Forum with Tennessee State Legislature on ``Health in Tennessee: The Impact of Climate Change.'' (organized by Papasan Institute for Government Relations, U. Memphis), June 3.
\entry*[2008]Co-chair, Faculty Seminar on ``Technology, Commonweal, and the Transformation of Humanity'' Center for Ethics, Vanderbilt University (May 12--15 2008)
\entry*[2008]Session organizer \& chair, ``Quantifying Individual Emissions'' session, Consumption, Law, \& Environment Conference, Vanderbilt Law School (Apr.~17--19 2008).
\entry*[2008]Testimony on climate change, Tennessee House Committee on Conservation and Environment, Feb. 28.
\entry*[2007--2009]Member, Advisory Board on Environment, The Tennessean newspaper, Nashville TN.
\entry*[2007]Oak Ridge National Laboratory University Liaisons Meeting: Opportunities for Collaborative Research on Climate Change. Represented Vanderbilt University climate research, Sept 26.
\entry*[2006]Co-organizer, Nashville Forum on Christianity and the Environment, Scarritt-Bennett Center, Nashville TN, Sept. 30.
\entry*[2006]Session chair, ``Intra- and Inter-Generational Equity,'' Consumption, Law, \& Environment Roundtable, Vanderbilt Law School, Oct.~19--20.
\entry*[2006]Panelist, Genetically Modified Food, Belcourt Theatre, Nashville TN. Apr.~6.
\entry*[2005]Co-leader, Faculty seminar on Threats to Environmental Sustainability, Vanderbilt Center for the Study of Religion and Culture.
\entry*[2004--2007]Fellow, Center for the Study of Religion and Culture and core member, Ecology and Spirituality research group.
\entry*[2004--2009]Writing Advisory Board, Vanderbilt University.
%\entry*[1999--2000]Consultant to Burke Mays Assoc., Designed and implemented system for compression and transmission of clinical EEG data, Nashville TN.
\entry*[1999--2000]Vanderbilt Working Group on Amide Resonances in Laser Surgery, Vanderbilt University.
\entry*[1997]Chair, Program Session on Laser and Ion-Beam Processing, ASM Materials Week '97, Indianapolis, IN.
\entry*[1996]Co-Chair, Program Session on Laser and Ion-Beam Processing, ASM Materials Week '96, Cincinnati, OH.
\entry*[1996]Organizing Committee, 5$^{\mbox{\scriptsize th}}$ Annual Workshop of the Consortium for Nanostructured Materials, Nashville TN.
\entry*[1995--1996]Environmental Studies Committee, Vanderbilt University.
\end{rubric}
