%
% !TeX root = Gilligan_CV_nc_2017.tex
%
\begin{enumerate}
    \item 
    \textdagger\
    *E.K. Burchfield and \textbf{J.M. Gilligan}, 
    \enquote{Agricultural Adaptation to Drought in the Sri Lanakan Dry ZOne},
    Applied Geography, \textbf{77}, 92--100 (2016). 
    \nolinkurl{doi 10.1016/j.apgeog.2016.10.003}
%
    \item
    \textdagger\
    D.J. Hess, *C.A. Wold, *J. Nay, *S. Worland, \textbf{J. Gilligan}, and G.M. Hornberger, 
    \enquote{Drought, Risk, and Institutional Politics in the American Southwest},
    Sociological Forum \textbf{31}, 807--831 (2016).
    \nolinkurl{doi 10.1111/socf.12274}
%
    \item
    \textdagger\
    *L. Benneyworth, , \textbf{J. Gilligan}, J.C. Ayers, S. Goodbred, *G. George, A. Carrico, Md.R. Karim, F. Akter, *D. Fry, K. Donato, and *B. Piya,
    \enquote{Drinking Water Insecurity: Water Quality and Access in Coastal South-Western Bangladesh},
    International Journal of Environmental Health Research \textbf{26}, 508--524 (2016).
    \nolinkurl{doi 10.1080/09603123.2016.1194383}
%
    \item 
    \textdagger\ 
    *T. Gunda, G.M. Hornberger, and \textbf{J.M. Gilligan}, 
    \enquote{Spatiotemporal Patterns of Agricultural Drought in Sri Lanka: 1881--2010,}
    International Journal of Climatology \textbf{36}, 563--575 (2016).
    \nolinkurl{doi:10.1002/joc.4365}
%
    \item 
    \textdagger\
    G.M. Hornberger, D.J. Hess, and \textbf{J.M. Gilligan}, 
    \enquote{Water Conservation and Hydrological Transitions in Cities in the United States,}
     Water Resources Research \textbf{51}, 4635--4649 (2015).
%
    \item 
    M.P. Vandenbergh and \textbf{J.M. Gilligan}, 
    \enquote{Beyond Gridlock,}
    Columbia Journal of Environmental Law
    \textbf{40}, 217--303 (2015).
%
    \item 
    \textdagger\ 
    *L.W. Auerbach, S.L. Goodbred, Jr., D.R. Mondal, C.A. Wilson, *K.R. Ahmed, K. Roy, M.S. Steckler, C. Small, \textbf{J.M. Gilligan}, and B.A. Ackerly,
    \enquote{Flood risk of natural and embanked landscapes on the Ganges-Brahmaputra tidal delta plain,}
    Nature Climate Change
    \textbf{5}, 153--157 (2015).
%
    \item 
    M.P. Vandenbergh, K.E. Toner, and \textbf{J.M. Gilligan}, 
    \enquote{Energy and Climate Change: A Climate Prediction Market,}
    UCLA Law Review 
    \textbf{61}, 1962--2017 (2014).
%
    \item 
    \textbf{J.M. Gilligan} and M.P. Vandenbergh, 
    \enquote{Accounting for political feasibility in climate instrument choice,}  
    Virginia Environmental Law Journal
    \textbf{32}, 1--26 (2014).
%
    \item
    M.P. Vandenbergh and \textbf{J.M. Gilligan}, 
    \enquote{Macro-risks: The challenge for rational risk regulation,}  
    Duke Environmental Law and Policy Forum
    \textbf{21}, 401--431 (2011). 
%	
    \item
    A.R. Carrico, M.P. Vandenbergh, P.C. Stern, G.T. Gardner, T. Dietz, and \textbf{J.M. Gilligan}, 
    \enquote{Energy and climate change: Key lessons for implementing the behavioral wedge,}  
    Journal of Energy \& Environmental Law \textbf{2}, 61--67 (2011). 
%	
\iffalse
    \item
    M.P. Vandenbergh, P.C. Stern, G.T. Gardner, T.~Dietz, and \textbf{J.M. Gilligan}, 
    \enquote{Implementing the behavioral wedge,}  
    Environmental Forum \textbf{28}, 54--63 (Jul/Aug~2011).\ 
    \textbf{\scshape Note:} \emph{Reprint of Vandenbergh et al., Environ. L. Rep.\ \textbf{40}, 10\,547 (2010) as featured cover story for summmer reading issue.}  
\fi
%	
    \item
    M.P. Vandenbergh, P.C. Stern, G.T. Gardner, T.~Dietz, and \textbf{J.M. Gilligan}, 
    \enquote{Implementing the behavioral wedge: Designing and adopting effective carbon emissions reduction programs,}  
    Environmental Law Reporter
    \textbf{40}, 10\,547--54 (2010).  
    \emph{Selected by Environmental Law Institute to reprint as the featured cover story of the 2010 summer reading issue for policymakers of Environmental Forum.}
%	
    \item
    \textdagger\
    P.C. Stern, G.T. Gardner, M.P. Vandenbergh, T.~Dietz, and \textbf{J.M. Gilligan},
    \enquote{Design principles for carbon emissions reduction programs,}  
    Environmental Science and Technology \textbf{44}, 4847--48 (2010).  
%	
	\item
    \textbf{J.~Gilligan}, T.~Dietz, G.~Gardner, P.~Stern, and M.~Vandenbergh, 
	\enquote{The behavioral wedge: best policies to promote voluntary greenhouse gas reductions by individuals and households,}  
      Significance \textbf{7}, 17--20 (2010). 
      {\bfseries\scshape Note:} \emph{Named one of the best papers of 2009 by Significance.}  
%	
    \item
    \textdagger\ 
    T.~Dietz, G.~Gardner, \textbf{J.~Gilligan}, P.~Stern, and M.~Vandenbergh, 
    \enquote{Household actions can provide a behavioral wedge to rapidly reduce {U}.{S}. carbon emissions,}  
     Proc.\ Nat'l.\ Acad.\ Sci.{} \textbf{106}, 18\,452--18\,456 (2009).
%	
    \item
    \textdagger\ 
    *M.R. Holcomb, *M.C. Woods, *I.~Uzelac, J.P. Wikswo, \textbf{J.M. Gilligan}, and V.Y. Sidorov, 
    \enquote{The potential of dual camera systems for multimodal imaging of cardiac electrophysiology and metabolism,} 
    Exper.\ Biol.\ \& Med.{} \textbf{234}, 1355--1373 (2009). 
    {\bfseries\scshape Note:} \emph{Selected by the editors as the feature article of the month.}  
%	
    \item
    \textdagger\ 
    *A.R. Carrico, *P.~Padgett, M.P. Vandenbergh, \textbf{J.~Gilligan}, and K.A. Wallston, 
    \enquote{Costly myths: an analysis of idling beliefs and behavior in personal motor vehicles,}  
    Energy Policy \textbf{37}, 2881--2888 (2009).  
%	
    \item
    M.P. Vandenbergh, J.~Barkenbus, and \textbf{J.M. Gilligan}, 
    \enquote{Individual carbon emissions: The low-hanging fruit,}  
    UCLA Law Review \textbf{55}, 1701--1758 (2008).  
%	
    \item
    \textdagger\ 
    *D.N. Mashburn, *S.~Hinkson, *M.C. Woods, \textbf{J.M. Gilligan}, *M.R. Holcomb, and J.P. Wikswo, 
    \enquote{A high-voltage cardiac stimulator for field shocks of a whole heart in a bath,}  
    Rev. Sci. Instrum.\ \textbf{78}, 104\,302--104\,309 (2007).  
%	
	\item
    \textbf{J.M. Gilligan}, 
	\enquote{Flexibility, clarity, and legitimacy: Considerations for managing nanotechnolgy risks,}  
    Environmental Law Reporter \textbf{36}, 10\,924--10\,930 (2006).  
%	
	\item
	\textdagger\ 
    E.~Sobol, A.~Sviridov, M.~Kitai, \textbf{J.M. Gilligan}, G.S. Edwards, and N.H. Tolk, 
    \enquote{Time-resolved light scattering measurements of cartilage and cornea denaturation due to free-electron laser radiation,}  
    J. Biomed.\ Opt.\ \textbf{8}, 216--222 (2003). 
%	
    \item
    \textdagger\ 
    A. Cricenti, R. Generosi, M. Luce, P. Perfetti, G. Margaritondo, D. Talley, J.S. Sanghera,  I.D. Aggarwal, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{Surface characterisation by near-field microscopy and atomic force microscopy,} 
    Adv.\ Sci.\ Technol.\ \textbf{32}, 183--192 (2003).
%
    \item 
    \textdagger\ 
    *G. Mensing, \textbf{J. Gilligan}, P. Hari, *E. Hurt, G. L\"upke, S. Pantelides, N. Tolk, and P.C. Taylor, 
    \enquote{Defect transition energies and the density of electronic states in hydrogenated amorphous silicon,} 
    J. Non-Cryst.\ Solids \textbf{299}, 621--625 (2002).
%
    \item
    \textdagger\ 
    *J. Sturmann, *Z. Marka, *M. Albert, R.G. Albridge, \textbf{J.M. Gilligan}, G. Luepke, S. Pantelides, N. Tolk, and P. Taylor,
    \enquote{Infrared free-electron laser photoablation of diamond films,}
    J. Non-Cryst. Solids \textbf{299}, 621--625 (2002).
%
    \item
    \textdagger\ 
    A.~Cricenti, R.~Generosi, M.~Luce, P.~Perfetti, G.~Margaritondo, D.~Talley, J.~Sanghera, I.~Aggarwal, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{Spectroscopic scanning near-field optical microscopy with a free-electron laser: {CH$_2$}~bond imaging in diamond films,}  
    J. Microsc.\ \textbf{202}, 446--450 (2001). 
%
    \item
    \textdagger\ 
    D.B. Talley, L.B. Shaw, J.S. Sanghera, I.D. Aggarwal, A. Cricenti, R. Generosi, M. Luce, G. Margaritondo, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{Scanning near-field infrared microscopy using chalcogenide fiber tips,} 
    Materials Lett.\ \textbf{42}, 339--344 (2000).
%	
    \item
    \textdagger\ 
    G. L\"upke, *C. Parks Cheney, *J. Sturman, *J.C. Keay, \textbf{J.M. Gilligan}, L.C. Feldman, and N.H. Tolk, 
    \enquote{Materials science at the WM Keck Free-Electron Laser: Infrared wavelength-selective materials modification,} 
    Condensed Matter Theories \textbf{14}, 349--364 (2000).
%	
    \item
    \textdagger\ 
    A.~Cricenti, R.~Generosi, G.~Herold, P.~Chiaradia, P.~Perfetti, G.~Margaritondo, \textbf{J.M. Gilligan}, and N.H. Tolk,
    \enquote{Chemical contrast observed at a {III-V} heterostructure by scanning near-field optical microscopy,}  
    Phys.\ Stat.\ Solidi a-Appl.\ Res.\ \textbf{175}, 345--9 (1999). 
%	
    \item
    \textdagger\ 
    A.~Cricenti, R.~Generosi, P.~Perfetti, G.~Margaritondo, J.~Almeida, \textbf{J.M. Gilligan},  N.H. Tolk, C.~Coluzza, M.~Spajer, D.~Courjon, and I.D. Aggarwal, 
    \enquote{Interface applications of scanning near-field optical microscopy with a free-electron laser,}  
    Phys.\ Stat.\ Solidi a-Appl.\ Res.\ \textbf{175}, 317--29 (1999). 
%	
    \item
    \textdagger\ 
    *S.~Marka, *C.P. Cheney, *W.~Wang, G.~L\"upke, \textbf{J.~Gilligan}, *Y.~Yao, and N.H. Tolk, 
    \enquote{Nonlinear energy-selective nanoscale modifications of materials and dynamics in metals and semiconductors,}  
    Sov.\ Phys.\ Tech.\ Phys.\ \textbf{44}, 1069--72 (1999). 
%	
    \item
    \textdagger\ 
    D.T. Schaafsma, R.~Mossadegh, J.S. Sanghera, I.D. Aggarwal, \textbf{J.M. Gilligan}, N.H. Tolk, M.~Luce, R.~Generosi, P.~Perfetti, A.~Cricenti, and G.~Margaritondo, 
    \enquote{Singlemode chalcogenide fiber infrared {SNOM} probes,}  
    Ultramicroscopy \textbf{77}, 77--81 (1999). 
%	
    \item
    \textdagger\ 
    D.T. Schaafsma, R.~Mossadegh, J.S. Sanghera, I.D. Aggarwal, M.~Luce, R.~Generosi, P.~Perfetti, A.~Cricenti, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{Fabrication of single-mode chalcogenide fiber probes for scanning near-field infrared optical microscopy,}  
    Opt.\ Eng.\ \textbf{38}, 1381--5 (1999). 
%	
    \item
    \textdagger\ 
    A.~Cricenti, R.~Generosi, C.~Barchesi, M.~Luce, M.~Rinaldi, C.~Coluzza, P.~Perfetti, G.~Margaritondo, D.T. Schaafsma, I.D. Aggarwal, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{First experimental results with the free electron laser coupled to a scanning near-field optical microscope,}  
    Phys.\ Stat.\ Solidi a-Appl.\ Res.\ \textbf{170}, 241--7 (1998). 
%	
    \item
    \textdagger\ 
    A.~Cricenti, R.~Generosi, P.~Perfetti, \textbf{J.M. Gilligan}, N.H. Tolk, C.~Coluzza, and G.~Margaritondo, 
    \enquote{Free-electron-laser near-field nanospectroscopy,}  
    Appl.\ Phys.\ Lett.\ \textbf{73}, 151--3 (1998). 
%	
    \item
    \textdagger\ 
    *W.~Wang, G.~L\"upke, M.~Di~Ventra, S.T. Pantelides, \textbf{J.M. Gilligan}, N.H. Tolk, I.C. Kizilyalli, P.K. Roy, G.~Margaritondo, and G.~Lucovsky, 
    \enquote{Coupled electron-hole dynamics at the {Si$/$SiO$_2$} interface,}  
    Phys.\ Rev.\ Lett.\ \textbf{81}, 4224--7 (1998). This was principally Wang's and L\"upke's work. I contributed to data analysis and writing the paper.
%	
    \item
    \textdagger\ 
    *Y.~Yao, *Z.~Hargitai, *M.~Albert, R.G. Albridge, A.V. Barnes, \textbf{J.M. Gilligan}, *B.P. Ferguson, G.~L\"upke, *V.D. Gordon, N.H. Tolk, J.C. Tully, G.~Betz, and W.~Husinsky, 
    \enquote{New molecular collisional interaction effect in low-energy sputtering,}  
    Phys.\ Rev.\ Lett.\ \textbf{81}, 550--3 	  (1998).
%	
    \item
    \textdagger\ 
    *J.~Sturmann, R.G. Albridge, A.V. Barnes, J.L. Davidson, \textbf{J.M. Gilligan}, G.~L\"upke, *A.~Ueda, and N.H. Tolk, 
    \enquote{Infrared wavelength-selective photodesorption on diamond surfaces,}
    Appl.\ Surf.\ Sci.\ \textbf{129}, 59--63 (1998). 
%	
    \item
    \textdagger\ 
    N.H. Tolk, *Z.~Hargitai, *Y.~Yao, *B.~Pratt-Ferguson, *M.M. Albert, R.G. Albridge, A.V. Barnes, \textbf{J.M. Gilligan}, *V.D. Gordon, G.~L\"upke, A.~Puckett, J.~Tully, G.~Betz, and W.~Husinsky, 
    \enquote{Molecular effects in measured sputtering yields on gold at near threshold energies,}  
    Izv.\ Akad.\ Nauk.\ Ser.\ Fiz.\ \textbf{62}, 676--9 (1998). 
%	
    \item
    \textdagger\ 
    *C.M. Volk, J.W. Elkins, D.W. Fahey, G.S. Dutton, \textbf{J.M. Gilligan}, M.~Loewenstein, J.R. Podolske, K.R. Chan, and M.R. Gunson, 
    \enquote{Evaluation of source gas lifetimes from stratospheric observations,}
    J. Geophys.\ Res.\ Atmos.\ \textbf{102}, 25\,543--64 (1997). 
%	
    \item
    \textdagger\ 
    *J.~Sturmann, R.G. Albridge, A.V. Barnes, \textbf{J.~Gilligan}, *M.T. Graham, J.T. McKinley, *W.~Wang, *X.~Yang, N.H. Tolk, J.L. Davidson, and G.~Margaritondo, 
    \enquote{Photoexcitation spectroscopy and material alteration with free-electron laser,}  
    Act.\ Phys.\ Polon.\ A \textbf{91}, 689--96 (1997).
%	
    \item
    \textdagger\ 
    *C.M. Volk, J.W. Elkins, D.W. Fahey, R.J. Salawitch, G.S. Dutton, \textbf{J.M. Gilligan}, M.H. Proffitt, M.~Loewenstein, J.R. Podolske, K.~Minschwaner, J.J. Margitan, and K.R. Chan, 
    \enquote{Quantifying transport between the tropical and mid-latitude lower stratosphere,}  
    Science \textbf{272}, 1763--8 (1996).
%	
    \item
    \textdagger\ 
    J.W. Elkins, D.W. Fahey, \textbf{J.M. Gilligan}, G.S. Dutton, T.J. Baring, *C.M. Volk, R.E. Dunn, R.C. Myers, S.A. Montzka, P.R. Wamsley, A.H. Hayden, J.H. Butler, T.M. Thompson, 
T.H. Swanson, E.J. Dlugokencky, P.C. Novelli, D.F. Hurst, J.M. Lobert, S.J. Ciciora, R.J. McLaughlin, T.L. Thompson, R.H. Winkler, P.J. Fraser, L.P. Steele, and *M.P. Lucarelli,
    \enquote{Airborne gas chromatograph for \emph{in situ\/} measurements of long-lived species in the upper troposphere and lower stratosphere,}  
    Geophys.\ Res.\ Lett.\ \textbf{23}, 347--50 (1996). 
%	
    \item
    \textdagger\ 
    E.L. Woodbridge, J.W. Elkins, D.W. Fahey, L.E. Heidt, S.~Solomon, T.J. Baring, T.J. Gilpin, W.H. Pollock, S.M. Schauffler, E.L. Atlas,
    \enquote{Estimates of total organic and inorganic chlorine in the lower stratosphere from \emph{in situ\/} measurements during \textsc{aase ii},}  
    M.~Lowenstein, J.R. Podolske, C.R. Webster, R.D. May, \textbf{J.M. Gilligan}, S.A. Montzka, K.A. Boering, and R.J. Salawitch, 
    J.\ Geophys.\ Res. \textbf{100}, 3057--64 (1995). 
%	
    \item
    \textdagger\ 
    U.~Eichmann, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, W.M. Itano, D.J. Wineland, and M.G. Raizen, 
    \enquote{Young's interference experiment with light scattered from two atoms,}
    Phys.\ Rev.\ Lett.\ \textbf{70}, 2359--62 (1993). 
%	
    \item
    \textdagger\ 
    D.~Shiner, \textbf{J.M. Gilligan}, *B.M. Cook, and W.~Lichten, 
    \enquote{{H$_2$}, {D$_2$}, and {HD} ionization potentials by accurate calibration of several iodine lines,}  
    Phys.\ Rev.\ A \textbf{47}, 4042--5 (1993). 
%	
    \item
    \textdagger\ 
    W.M. Itano, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, F.L. Moore, and M.G. Raizen, 
    \enquote{Quantum projection noise: Population fluctuations in two-level systems,}  
    Phys.\ Rev.\ A \textbf{47}, 3554--70 (1993). 
%	
	\item
	\textdagger\ 
	W.M. Itano, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, D.J. Heinzen, F.L. Moore, M.G. Raizen, and D.J. Wineland, 
    \enquote{Ultra-high precision spectroscopy for fundamental physics,}  
	Hyperfine Interactions \textbf{78}, 211--20 (1993).
%	
	\item
	\textdagger\ 
	W.M. Itano, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, D.J. Heinzen, F.L. Moore, M.G. Raizen, and D.J. Wineland, 
    \enquote{Quantum measurements of trapped ions,}  
	Vistas in Astronomy pp. 169--83 (1993). 
%	
    \item
    \textdagger\ 
    \textbf{J.M. Gilligan} and E.E. Eyler, 
    \enquote{Precise determinations of ionization potentials and {$EF$} state energy levels of {H$_2$}, {HD}, and {D$_2$},}  
    Phys.\ Rev.\ A \textbf{46}, 3676--90 (1992).
%	
    \item
    \textdagger\ 
    M.G. Raizen, \textbf{J.M. Gilligan}, J.C. Bergquist, W.M. Itano, and D.J. Wineland, 
    \enquote{Ionic crystals in a linear {P}aul trap,}  
    Phys.\ Rev.\ A \textbf{45}, 6493--501 (1992). 
%	
    \item
    \textdagger\ 
    M.G. Raizen, \textbf{J.M. Gilligan}, J.C. Bergquist, W.M. Itano, and D.J. Wineland, 
    \enquote{Linear trap for high-accuracy spectroscopy of stored ions,}  
    J.\ Modern.\ Opt.\ \textbf{39}, 233--42 (1992). 
%	
    \item
    \textdagger\ 
    \textbf{J.M. Gilligan} and E.E. Eyler, 
    \enquote{High-resolution three-photon spectroscopy and multiphoton interference in molecular hydrogen,}  
    Phys.\ Rev.\ A \textbf{43}, 6406--9 (1991). 
%	
    \item
    \textdagger\ 
    E.~McCormack, \textbf{J.M. Gilligan}, C.~Cornaggia, and E.E. Eyler,
    \enquote{Measurement of high Rydberg states and the ionization potential of {H$_2$},}  
    Phys.\ Rev.\ A \textbf{39}, 2260--3 (1989). 
%	
\iffalse
    \item
    E.F. McCormack, E.E. Eyler, and \textbf{J.M. Gilligan}, 
    \enquote{Precise photodissociation and multiphoton spectroscopy of $\H_2$},
    J. Opt. Soc. B Opt. Phys.\ \textbf{4}, 80 (1987).  
\fi
%	
    \item
    \textdagger\
    E.E. Eyler, \textbf{J.M. Gilligan}, E.~McCormack, A.~Nussenzweig, and E.~Pollack, 
    \enquote{Precise two-photon spectroscopy of {$E\leftarrow X^*$} intervals in {H$_2$},}  
    Phys.\ Rev.\ A \textbf{36}, 3486--89 (1987).  
%
\end{enumerate}


