%
% !TeX root = Gilligan_CV_2015.tex
%
The idea of adapting Hawthorne's \emph{Scarlet Letter\/} to the stage originated with Carol Gilligan. Writing the script for Scarlet Letter play and libretto for Pearl opera was a joint project equal contributions from each of us. Amy Scurria wrote the music for Pearl. Sara Jobin served as producer both for assembling the librettists and composer and also for organizing the public performances of Pearl.
\begin{enumerate}
\item  2013: \emph{Pearl}, Concert performance of the opera. Music by Amy Scurria, libretto by Carol Gilligan and Jonathan Gilligan. Maureen O'Flynn, soprano; John Bellemer, Tenor; Marnie Breckenridge, soprano; John Cheek, Bass-Baritone; Michael Corvino, Bass; Olivia Marchione, Child Soprano. Sara Jobin, Conductor, and Producer. At Shakespeare \& Company, Lenox MA, Aug.~5.
\item 2013: \emph{Pearl}, Excerpts from opera performed at University of Shanghai for Science and Technology as part of a cultural exchange program. John Bellemer, Tenor; Li Xin, Soprano; Wang Yang, Bass-Baritone; Lin Shu, Soprano; Charmaine, Child Soprano. March 21.
\item  2012: \emph{Pearl}, Concert performance of the opera. Music by Amy Scurria, libretto by Carol Gilligan and Jonathan Gilligan. Maureen O'Flynn, soprano; Marnie Breckenridge, soprano; John Bellemer, Tenor; John Cheek, Bass-Baritone; Olivia Marchione, Child Soprano; John Demler, Baritone; Jack Brown, Baritone; Sara Jobin, Piano, Conductor, and Producer. At Shakespeare \& Company, Lenox MA, Aug.~13.
\item 2011: The Prime Stage (Pittsburgh, PA) produces \emph{The Scarlet Letter}, by Carol Gilligan and Jonathan Gilligan. Katie Mueller, director. 9~performances.
\item 2011: South-Central Graduate Music Consortium Composer's Concert, Univ.\ N. Carolina Chapel Hill. \emph{Pearl}, performance of opera as work-in-progress (Amy Scurria, music; Carol Gilligan and Jonathan Gilligan, libretto). Emily Siar, Soprano; Noelle Harb, Soprano; Ping Fu, Soprano; Tim Hambourger, Piano. 
\item 2010--2011: The National Players produce \textit{The Scarlet Letter\/} as part of its 61st season. 31~performances.
\item 2009: ``Prima le Parole:'' staged reading of work in progress, libretto excerpt from \emph{Pearl}, an opera inspired by Hawthorne's \emph{The Scarlet Letter}, by Carol Gilligan and Jonathan Gilligan. Center for Contemporary Opera and New York Society Library, Nov.~9. 
\item 2007: \emph{The Scarlet Letter\/} by Carol Gilligan and Jonathan Gilligan staged reading starring Marisa Tomei, Ron Cephas Jones, Bobby Cannavale, and Marin Ireland, directed by Leigh Silverman. Produced by The Culture Project as part of the ``Women Center Stage'' festival, New York City July 10--11.
\item 2006: \emph{The Scarlet Letter\/} by Carol Gilligan and Jonathan Gilligan workshop performance by The Little Theater of Winston-Salem, as part of New Horizons Performance Series, sponsored by the Thomas S. Kenan Institute for the Arts, North Carolina School of the Arts, Oct.~21--22.
\item 2005: Stage adaptation of \emph{The Scarlet Letter\/} by Carol Gilligan and Jonathan Gilligan, staged reading starring Marisa Tomei, directed by Weir Harman. Produced by The Culture Project, as part of the ``Women Center Stage'' festival, New York City Aug.\ 7--8.
\end{enumerate}