%
% !TeX root = Gilligan_CV.tex
%

Performances of \emph{The Scarlet Letter}, a stage adaptation of Hawthorne's novel by Carol Gilligan and Jonathan Gilligan and \emph{Pearl}, an opera by Amy Scurria, libretto by Carol Gilligan and Jonathan Gilligan:
\ifcredit

The idea of adapting Hawthorne's \emph{Scarlet Letter\/} to the stage originated with Carol Gilligan. The idea of adapting the play into an opera originated jointly with Sara Jobin, Carol Gilligan, and myself equally.

Writing the script for the play \emph{Scarlet Letter\/} and the libretto for the opera \emph{Pearl\/} were joint projects equal contributions from each of us.

Amy Scurria wrote all of the music for \emph{Pearl}. Sara Jobin served as producer both for assembling the librettists and composer and also for casting and organizing the public performances of
\emph{Pearl}.
\fi
\begin{description}
\item[2019] \emph{Scarlet Letter:\/} Fullerton College Classic Dramatic Series, Fullerton CA, Nov. 10--12. Michael Mueller, director. 3 performances.
\item[2019--2020] \emph{Scarlet Letter:\/} Classic Repertory Company, Watertown MA, repertory season. Clay Hopper, director.
\item[2016--2017] \emph{Scarlet Letter:\/} Classic Repertory Company, Watertown MA, repertory season. Clay Hopper, director.
\item[2013] \emph{Pearl:\/} Concert performance at Shakespeare \& Company, Lenox MA, Aug.~5.
  Maureen O'Flynn, soprano; John Bellemer, Tenor; Marnie Breckenridge, soprano; John Cheek, Bass-Baritone; Michael Corvino, Bass; 
  Olivia Marchione, Child Soprano. Sara Jobin, Conductor, Piano, and Producer.
\item[2013] \emph{Pearl:\/}, Excerpts performed at University of Shanghai for Science and Technology,  March 21, 
  as part of a cultural exchange program sponsored by U.S. Department of State. 
  John Bellemer, Tenor; Li Xin, Soprano; Wang Yang, Bass-Baritone; Lin Shu, Soprano; Charmaine, Child Soprano.
\item[2012] \emph{Pearl:\/} Concert performance at Shakespeare \& Company, Lenox MA, Aug. 13. 
  Maureen O'Flynn, soprano; Marnie Breckenridge, soprano; John Bellemer, Tenor; John Cheek, Bass-Baritone; 
  Olivia Marchione, Child Soprano; John Demler, Baritone; Jack Brown, Baritone; 
  Sara Jobin, Piano, Conductor, and Producer.
\item[2011] \emph{Scarlet Letter:\/} The Prime Stage, Pittsburgh, PA, Nov.~4--13. Katie Mueller, director. 9~performances.
\item[2011] \emph{Scarlet Letter:\/} South-Central Graduate Music Consortium Composer's Concert, Univ.\ N. Carolina Chapel Hill. 
  Emily Siar, Soprano; Noelle Harb, Soprano; Ping Fu, Soprano; Tim Hambourger, Piano.
\item[2010--2011] The National Players produce \textit{The Scarlet Letter\/} as part of its 61st season. 31~performances.
\item[2009] \emph{Pearl:\/} Staged reading of the libretto at ``Prima le Parole,'' Center for Contemporary Opera and New York Society Library, Nov.~9.
\item[2007] \emph{Scarlet Letter:\/} Staged reading at The Culture Project, New York City, as part of the ``Women Center Stage'' festival, July 10--11.
  Cast: Marisa Tomei, Ron Cephas Jones, Bobby Cannavale, and Marin Ireland.
  Leigh Silverman, director. Produced by The Culture Project 
\item[2006] \emph{Scarlet Letter:\/} Workshop performance by The Little Theater of Winston-Salem, as part of New Horizons Performance Series, 
  sponsored by the Thomas S. Kenan Institute for the Arts, North Carolina School of the Arts, Oct.~21--22. 2 performances.
\item[2005] \emph{The Scarlet Letter:\/} Staged reading at The Culture Project, New York City, as part of the ``Women Center Stage'' festival, 
  Aug.\ 7--8. 2 performances.
  Starring: Marisa Tomei.
  Weir Harman, director. 2 performances.
\end{description}