\begin{description}
\item[2023--present] Professor, Dept.\ of Earth \& Environmental Sciences, Vanderbilt University.
\item[2023--present] Professor, Dept.\ of Civil \& Environmental Engineering (secondary), Vanderbilt University.
\item[2022--2023] The Alexander Heard Distinguished Service Professor,
  Vanderbilt University
\item[2016--2023] Associate Professor, Dept.\ of Civil \& Environmental Engineering (secondary), Vanderbilt University.
\item[2009--2023] Associate Professor, Dept.\ of Earth \& Environmental Sciences, Vanderbilt University.
\item[2008--2009] Research Assistant Professor, Dept.\ of Earth \& Environmental Sciences, Vanderbilt University.
\item[2003--2009] Senior Lecturer, Dept.\ of Earth \& Environmental Sciences, Vanderbilt University.
\item[2000--2003] The Robert T. Lagemann Assistant Professor of Living State Physics, Dept.\ of Physics \& Astronomy, Vanderbilt University.
\item[1996--1998] Associate Director, Center for Molecular and Atomic Studies at Surfaces, Vanderbilt University.
\item[1995--2000] Research Assistant Professor, Dept.\ of Physics \& Astronomy, Vanderbilt University.
\item[1994--1995] Lecturer, Dept.\ of Physics \& Astronomy, Vanderbilt University.
\item[1993--1994] Postdoctoral Research Associate, Cooperative Institute for Research in Environmental Science, National Oceanic \& Atmospheric Administration and the University of Colorado. Mentors: James W. Elkins (NOAA) and David W. Fahey (NOAA).
\item[1991--1993] National Research Council Postdoctoral Associate, National Institute of Standards \& Technology. Mentor David J. Wineland.
\item[1985--1991] Graduate Student/Teaching Assistant/Research Assistant, Yale University. Mentor Edward E. Eyler.
\item[1983--1985] High school teacher, Commonwealth School, Boston MA.
\end{description}
