\item Ishita Dash (Ph.D. 2022, Civil \& Environmental Engineering, Dissertation committee).
\item Charles Doktycz (Ph.D. 2022, Civil \& Environmental Engineering, Dissertation committee).
\item Paul Johnson (Ph.D. 2021, Civil \& Environmental Engineering, Dissertation committee).
\item Matthew Dietrich (Ph.D. 2021, Earth \& Environmental Sciences, Dissertation committee).
\item Thomas Rechtman (M.S. 2021, Earth \& Environmental Sciences, Dissertation committee).
\item Ke ``Jack'' Ding (Ph.D. 2020, Environmental Engineering, Dissertation committee).
\item George Duffy (Ph.D. 2020, Earth \& Environmental Sciences, Dissertation committee).
\item Rachel McKane (Ph.D. 2020, Sociology, Dissertation committee).
\item Jennifer Bradham (Ph.D. 2019, Earth \& Environmental Sciences, Dissertation committee).
\item Leslie Gillespie-Marthaler (Ph.D. 2019, Environmental Engineering, Dissertation committee).
\item Kate Nelson (Ph.D. 2018, Environmental Engineering, Dissertation Committee, Dissertation committee).
\item Scott C. Worland (Ph.D. 2018, Environmental Engineering, Dissertation committee).
\item Christian Hung (former Ph.D. Student, Economics, Dissertation committee).
\item Brooke Patton (M.S. 2017, Earth \& Environmental Sciences, committee).
\item Leslie Duncan (Ph.D. 2017, Environmental Engineering, Dissertation committee).
\item Thushara Gunda (Ph.D. 2017, Environmental Engineering, Dissertation committee).
\item Jennifer Pickering (Ph.D. 2016, Earth \& Environmental Science, Dissertation committee).
\item Elena Wilmot (former Ph.D. student, Earth \& Environmental Sciences, Dissertation committee).
\item Kendra Abkowitz (Ph.D. 2015, Environmental Engineering, Dissertation committee).
\item Elizabeth Stone (M.S. 2015, Earth \& Environmental Science, Committee).
% \item John Jacobi (Ph.D. 2014, Environmental Engineering, Dissertation Committee and co-advisor).
\item Gregory George (M.S. 2014, Earth \& Environmental Science, Committee).
\item Shelley Donohue (M.S. 2013, Earth \& Environmental Science, Committee).
\item Courte Voorhees (Ph.D. 2012,  Community Research \& Action, Dissertation committee).
\item Ryan Haupt (M.S. 2012, Earth \& Environmental Science, Committee).
\item Patricia Conway (former Ph.D. student, Community Research \& Action, Dissertation committee).
\item Luis Fong (Ph.D. 2005, Physics, Dissertation committee).
\item Andrew Rose (Ph.D. 2001, Physics, Dissertation committee).
\item Christine Cheney (Ph.D. 2001, Physics, Dissertation committee).
