% !TeX document-id = {d206223e-80cd-48b7-93a5-45cd17290331}
% !TeX program = lualatex
% !BIB program = biber
\NeedsTeXFormat{LaTeX2e}
\documentclass[10pt]{article}
% \usepackage{newclude}
\newif\ifcredit
\creditfalse

% \usepackage{jglucida}
\usepackage[LGR,LY1]{fontenc}
\usepackage[osf]{noto}
\usepackage{pifont}
%\setmonofont{Latin Modern Mono}
%\usepackage[ttdefault=true]{AnonymousPro}
%\setmonofont{Anonymous Pro}[Scale=MatchUppercase, ScaleAgain=0.9]
%\usepackage{inconsolata}
%\setmonofont{InconsolataN}[Scale=MatchLowercase]
\usepackage[bold-style=ISO]{unicode-math}
\usepackage{fontspec}

\setmathfont{Cambria Math}

\usepackage{microtype}

\newcommand{\thedate}{Feb.\ 19, 2023}
\newcommand{\fullname}{Jonathan M. Gilligan}

\input{alt_preamble}

\fancyfoot[R]{}
\addbibresource{jgpubs.bib}

%
\title{}
\date{\thedate}
\author{Jonathan Mark Gilligan}
\begin{document}
\maketitle

\section{Contact Information}
\input{short_contact}

\section{Degrees Earned}
\begin{description}
	\input{short_degrees}
\end{description}
\section{Employment History}
\input{short_employment}

\section{Honors and Awards}
\begin{description}
\item[2022] The Alexander Heard Distinguished Service Professor Award,
  Vanderbilt University.
\item[2018] The Chancellor's Award for Research, Vanderbilt University.
\item[2017] The Morrison Prize for the highest impact paper of the year
  on sustainability law and policy.
\item[1998] Outstanding Scientific Paper Award, NOAA Environmental Research
  Labs.
\item[1995] NASA Group Achievement Award for outstanding accomplishments and
  contributions to the ASHOE/MAESA airborne research mission.
\item[1991--1993] National Research Council Postdoctoral Associate
\item[1985--1986] J.W. Gibbs Fellow, Yale University
\end{description}

\section{Summary of Published Scholarship}
    One book, 77~journal papers, 3~book chapters, 20~substantive papers in
    conference proceedings, 2~patents, 7~open-source software packages.
    \subsection{Citations and H-Index}
    \input{short-citation-metrics}
	%
  \subsection[Selected Publications]{Selected Recent Publications}
    \begin{refsection}
    \nocite{
      vandenbergh:2017:beyond.politics,
      best:2022:random.forest,
      best:2021:random.forest,
      best:2021:WSC,
      gilligan:2021:collaboration,
      ding:2021:Cape-Town,
      martinez:2021:transit,
      schenuit:2021:geoengineering,
      elsawah:2020:grand.challenges,
      carrico:marriage:2020,
      gilligan:2020:assessing.private.governance,
      gilligan:2020:beyond.wickedness,
      nielsen:2020:mitigation.analysis,
      gilligan:2019:diet,
      gilligan:2018:water.conservation,
      gilligan:2018:human.factor,
      ruhl:2018:topic.modeling,
      ackerly:2017:climate.community,
      burchfield:2016:ag.adaptation,
      burchfield:2016:abm,
      gilligan:2015:flood.partsim,
      benneyworth:2016:drinking.water,
      auerbach:2015:polder,
      nay:2015:decision.models,
      dietz:2009:behavioral.wedge,
      }
    \printbibliography[heading=none]
    \end{refsection}
	%
  \subsection{Selected Recent Invited Presentations}
   45 invited presentations, including:
   \begin{itemize}
     \item ``The Race Towards Climate Justice,'' 2023 Clinton Global
       Initiative University (CGI-U) conference.
       March 3--5, 2023.
\item ``Modeling Behavior Change in Socio-Environmental Systems.''
Invited talk, Second Coastlines and People Workshop on Identifying Interoperability and Data Needs of Interdisciplinary Models for
Understanding Vulnerability of Coastal Systems. Florida International
University (Sponsored by National Science Foundation). Oct. 4, 2022.
% (Host paid for travel, lodging, and meals).
\item ``Incorporating Human Behavior into Coupled Socio-Environmental Systems
Models.'' Keynote talk, National Socioenvironmental Synthesis Center
webinar on Methods in Socio-Environmental Systems Modeling.
June 20, 2022. A video of my talk and the panel discussion that followed, has been posted to the
SESYNC YouTube channel at \url{https://www.youtube.com/watch?v=rI994KY7ftE}
\item ``Integrating Machine Learning with Agent-Based Modeling to Understand
Human Impacts of Climate Change.'' Invited seminar, Florida International
University. May 25, 2021.
\item ``Accounting for Human Behavior in Models of Coupled Natural \& Human
Systems,'' Invited presentation at Workshop on Coastal Observation and
Modeling Systems, sponsored by NSF Coastlines and People program. Virtual
conference hosted by Florida International University, Miami, FL,
September 8, 2020. (98 attendees).
\item ``Managing Sediment for Sustainability,'' Invited virtual seminar,
International Centre for Climate Change and Development, Dhaka, Bangladesh,
July 20, 2020.
\item ``Beyond Wickedness: Managing Complex Systems and Climate Change,''
Invited presentation, co-delivered with Michael P. Vandenbergh. Vanderbilt
University Law Review Symposium on Governing Wicked Problems. Nashville, TN,
October 25, 2019.
\item ``The New Revolving Door," Invited presentation, co-delivered with
Michael P. Vandenbergh. Case-Western Reserve Law School Symposium on Fifty
Years of the Environmental Protection Agency. Cleveland, OH, October 18, 2019.
\item ``Agent-Based Modeling of Community Resilience and Environmental
Non-Migration,'' Invited presentation, First International Conference on
Environmental Non-Migration: Framework, Methods, and Cases, Technical
University of Dresden, June 19-21 2019.
\item ``Sediment Management and Sea-Level Rise,'' invited presentation, Fifth
Annual Gobeshona International Conference on Climate Knowledge, International
Centre for Climate Change and Development, Dhaka, Bangladesh, January 9, 2019.
\item Invited panelist, ``What Can an Individual Do to Help Limit Climate
Change,'' public panel discussion at Copenhagen Business School, Aug. 29,
2018.
\item Invited participant, Workshop on Household Actions to Reduce Greenhouse
Gas Emissions, Copenhagen Business School, Copenhagen Denmark, August 27--28
2018
% (Host paid for travel, lodging, and meals).
% \item International Symposium on Society and Resource Management (ISSRM), Salt Lake City, UT, June 17--21 2018.
\item Invited panelist, ``Re-envisioning `Sustainable' Deltas through Critical
Geography,'' American Association of Geographers Annual Conference, April
2018.
\item ``Carrot and Sticks in Private Climate Governance,'' invited
presentation, Joint Conference on Environmental Regulation. The Hagler
Institute for Advanced Study at the Texas A\&M University School of Law and
the Classical Liberal Institute at the New York University School of Law.
March 9--10, 2018.
% (Host paid for travel, lodging, and meals).
\item ``Energy and the Economy of Sri Lanka,'' invited presentation, Workshop
on Assessing Stakeholder Preferences in Planning of Energy Sector in Sri
Lanka, Colombo, Sri Lanka, August~11, 2017.
\item ``Understanding and Adapting to Water Scarcity at the Community Level,''
invited keynote presentation, Conference on Recognizing Climate Change Risk
of Dry Zone Farmers, Ministry of Disaster Management, Colombo, Sri Lanka,
August~10, 2017.
\item ``Planning for Environmental Stress and Disasters: The Importance of
Interdisciplinary Approaches,'' invited presentation to the Institute of Town
Planners of Sri Lanka and the Organization of Professional Associations of
Sri Lanka. Colombo, Sri Lanka, August~9, 2017.
\item ``Quantifying the Potential for Greenhouse Gas Emissions Reductions
through Private Governance,'' invited presentation to National Academies
Board on Environmental Change and Society. National Academies, Washington,
DC, July 11, 2017.
% (Host covered travel, lodging, \& meals).
\item  ``Connecting Human and Natural Systems: The Role of Agent-Based
Simulations,'' invited keynote talk, CSDMS 2017 Annual Meeting on Modeling
Coupled Earth and Human Systems. Boulder, CO. May 23--25 2017.
% (Host covered travel, lodging, meals, \& conference registration).
My talk is online at
\url{https://www.youtube.com/watch?v=v6i5_P_OOcU}.
\item  ``Dynamics of Individual and Collective Agricultural Adaptation to Water
Security,'' invited talk, Winter Simulation Conference 2016, Arlington, VA,
December~12, 2016.
   \end{itemize}

 \section{Selected Synergistic Activities}
 \begin{description}
   \item [2021--present] Principal Investigator, NSF Sustainable Regional
   Systems Planning Grant to work with state and local
   governments, businesses, and communities to improve resilient and
   equitable access to
   of electricity, transportation, and telecommunications in urban and rural communities in the Southeast.
   \item [2021--present] Co-Principal Investigator, NSF Future of Work at the
   Human-Technology Frontier Planning Grant to work with water-treatment
   utilities to develop interactive computational tools for training the
   next generation of water treatment operators, and to facilitate human
   decision-making about maintaining water quality in the face of
   climate change.
   \item [2021--present] Associate Editor for Climate Law and Policy,
\emph{Frontiers in Climate}.
   \item[2021--present] Co-Chair Interdisciplinary Climate Studies
   Curriculum Committee, Vanderbilt University. Developed a novel
   interdisciplinary major in climate studies that incorporates humanities,
   social-science, and natural-science perspectives.
   \item[2020--present] Director, Vanderbilt Climate and Society Grand
     Challenge Initiative.
     Leading a university initiative to bring scholars in humanities, social
     sciences and natural sciences together for collaborative scholarship and
     interdisciplinary teaching about climate change and its impacts on
     society.
  \item[2020--present] Contributor to Nashville Mayor's Sustainability Advisory
    Committee.
   \item [2020--present] Member, research partnership between Vanderbilt,
cities of Chattanooga and Nashville, and University of Tennessee, Chattanooga to improve the efficiency of public transit service.
   \item[2016--2021] External Advisory Committee,
     Urban Water Innovation Network, an NSF-sponsored sustainability research
     network with \$12.5 million in funding.
    \item [2019--2021] External Advisory Committee,
    Water Unaffordability in the United States, an interdisciplinary NSF-sponsored research project, Laura Senier, PI.
  \item[2019] Scientific Committee, First International Conference on Environmental Non-Migration. Dresden Germany, June 19--21, 2019.
  \item[2016--2019] Co-Principal Investigator, Vanderbilt Initiative for Smart-City Operations
     Research.
   \item[2018] Co-Chair, Environment and Sustainability Applications Track,
     Winter Simulation Conference. Goteborg, Sweden. Dec.\ 9--12, 2018.
\iffalse
  \item[2016--present] Organizing Committee, Annual Conference on Artificial
    Intelligence and the Law, Vanderbilt Law School.
\fi
\iftrue
  \item[2016--2022] Program Committee, Environmental and Sustainability
    Applications track, Winter Simulation Conference, co-sponsored by IEEE and
    INFORMS.
  \item[2018] Working Group on the Use of Socio-Environmental Systems Modeling
    in Actionable Science, National Socio-Environmental Synthesis Center.
\fi
 \end{description}
\end{document}
%% cv.tex ends here.
