\item Christopher Tasich (Ph.D. 2023, Earth \& Environmental Sciences) Principal  
  dissertation advisor, with co-advisor George Hornberger.
  Current position: U.S. Presidential Management Fellow at Environmental Protection Agency.
\item Wenwen ``Bowen'' He (Ph.D. 2023, Civil \& Environmental Engineering) 
  Principal dissertation advisor, with co-advisor Janey Camp.
  Current position: Solar power analyst.
\item Juan Mart\'inez (M.S. 2023, Civil \& Environmental Engineering).
  Thesis advisor.
\item Kelsea Best (Ph.D. 2022, Earth \& Environmental Sciences).
  Dissertation advisor.
  Current position: Assistant Professor, Department of Civil, Environmental, \& Geodetic
  Engineering and Department if City \& Regional Planning,
  The Ohio State University.
\item David Knorr (M.S. 2019, Earth \& Environmental Sciences).
  Thesis advisor.
  Current position: Data Scientist, Home Depot, Atlanta, GA.)
\item Emily Burchfield (Ph.D. 2017, Environmental Engineering).
  Dissertation advisor.
  Current position: Tenure-track Assistant Professor, Emory University, Department of Environmental Sciences).
\item John Nay (Ph.D. 2017, Integrated Computational Decision Science).
  Dissertation advisor.
  Current position: Founder and CEO, Brooklyn Artificial Intelligence Research and Brooklyn Investment Group, LLC..
\item Rachel Shumaker (M.S. 2017, Earth \& Environmental Sciences).
  Thesis advisor.
  Current position: Environmental Scientist, Dewberry Engineers, Blanch, NC.
% \item Kevona Belcher (M.S. Student, Environmental Engineering and Vanderbilt-Fisk Bridge Program, Advisor. Currently on extended medical leave).
\item Laura Benneyworth (Ph.D. 2016, Environmental Management and Policy).
  Dissertation advisor.
  Current position: Retired.
\item John Jacobi (Ph.D. 2014, Environmental Engineering).
  George Hornberger was Jacobi's primary advisor.
  I supervised research using agent-based modeling of farmer decision-making that formed one third of his dissertation.
  Current position: Managing Director, Reinsurance Solutions, Aon, PLC).
