%
% !TeX root = Gilligan_CV.tex
%
\subsubsection{Current Grants}
\begin{enumerate}
	%
	\item National Science Foundation: NSF-SRS 2115392,
	``Connecting Rural and Urban Environments for Equitable Access to Transportation, Telecommunications and Energy (CREEATTE).''
	Nov.~1, 2021--Oct.~31, 2022.
	Total funds: \$149,573. Direct costs: \$110,215. Indirect costs: \$39,358.
	Principal Investigator Jonathan Gilligan.
	%
	\item National Science Foundation: NSF-FW-HTF 2129083,
	``Integrating Practitioner Knowledge and Technology for the Future of Water Treatment.''
	Sept.~15, 2021--Sept.~14, 2022. 
	Total funds: \$150,000. Direct costs: \$105,890. Indirect costs: \$44,110.
	Principal Investigator Janey Camp.
    %
    \item National Science Foundation: NSF-CNH 1716909,
    ``Socioecological System Dynamics Related to Livelihood, Human Migration, and Landscape Evolution.''
    Sept.~1, 2017--Feb.~28, 2022.
    Total funds: \$1,498,721 over four and one half years. Vanderbilt portion: Direct costs: \$100,067. Indirect costs: \$57,083. Total funds: \$157,105.
    Principal Investigator Amanda Carrico (University of Colorado).
\begin{credit}
I am the principal investigator for the Vanderbilt portion of this project and my role is the lead in computational modeling and geospatial statistical analysis.
\end{credit}
    %
    \item Vanderbilt College of Arts \& Science,
    ``Climate and Society Grand Challenge Initiative.''
    18-month grant to develop interdisciplinary connections between Humanities, Social Sciences, and Natural Sciences around climate change and society.
    Jul.~1, 2020--Dec.~31, 2021.
    Total funds: \$60,000 over 18-months (direct costs: \$60,000, indirect costs: \$0).
    Principal Investigator Jonathan Gilligan
\begin{credit}
I am principal investigator and director of the project.
\end{credit}
    %
    \item Vanderbilt College of Arts \& Science,
    ``Global Ecology and Health Grand Challenge Initiative.''
    Jul.~1, 2020--Dec.~31, 2021.
    Total funds: \$75,000 over 18-months (direct costs: \$75,000, indirect costs: \$0).
    Principal Investigator John McLean.
\begin{credit}
18-month grant to develop interdisciplinary connections between biological sciences, environmental sciences, and social sciences around climate change and emergent infectious diseases.
I am co-investigator.
\end{credit}
    %
    \item Vanderbilt Trans-Institutional Project Grant,
    ``Vanderbilt Climate Prediction Market,''
    Jul.~1, 2020--Jun.~30, 2022.
    Total funds: \$200,000 over 2 years (direct costs: \$200,000, indirect costs: \$0).
    Principal Investigator Mark Cohen.
    %
    \item Vanderbilt Trans-Institutional Project Grant,
    ``Computational Thinking and Learning Initiative,''
    Jul.~1, 2019--Jun.~30, 2021.
    Total funds: \$200,000 over 2 years (direct costs: \$200,000, indirect costs: \$0).
    Principal Investigator Akos Ledeczi.
\end{enumerate}
%
\iffalse
\subsubsection{Pending Grant Proposals}
\begin{enumerate}
\end{enumerate}
\fi
%
\subsubsection{Previous Grants}
\begin{enumerate}
    %
    \item NSF Coastal SEES 1600319,
    ``Multiscale Modeling and Observations of Landscape Dynamics, Mass-Balance, and Network Connectivity for a Sustainable Gange-Brahmaputra Delta,''
    Aug.~1, 2016--Jul.~31, 2020.
    Total funds: \$810,211. Direct costs: \$532,163. Indirect costs: \$278,048.
    Principal Investigator Steven Goodbred.
\begin{credit}
I was co-principal investigator and my role is computational modeling, statistical data analysis, and risk analysis.
\end{credit}
    %
    \item National Science Foundation: NSF-EAR 1416964,
    ``Water Conservation and Hydrological Transitions in American Cities''
    Aug. 2014--Jul. 2017.
    Total funds: \$717,000 (direct costs: \$496,000, indirect costs: \$221,000).
    Principal Investigator George Hornberger.
\begin{credit}
I was a co-principal investigator and my role in the project is integration of physical and social science with emphasis on statistical analysis and
computer modeling of political and policy responses to water stress.
\end{credit}
    %
    \item Vanderbilt TIPS grant: ``VISOR: Vanderbilt Initiative on Smart-city Operations Research'' \$199,948 over 2~years (direct costs: \$199,948, indirect costs: \$0). Principal Investigator Gautam Biswas.
\begin{credit}
I was a co-principal investigator and my role is leading a research project studying the impact of gentrification on access to mass-transit in Nashville.
\end{credit}
    %
    \item Vanderbilt TIPS grant: ``Private Governance Approaches to Climate Change'' \$190,000 over 2~years (direct costs: \$190,000; indirect costs: \$0). Principal Investigator Michael Vandenbergh.
\begin{credit}
I was a co-principal investigator and my role is project design, statistical analysis, and coordinating undergraduate immersive experiences.
\end{credit}
	%
	\item "Climate Adaptation, Water-Energy Impacts, Perceptions and Behavior," Vanderbilt University Discovery Grant. Direct costs: \$99,532. No indirect costs. Period of Award: Mar. 2011--Feb. 2013. Principal Investigator George Hornberger.
\begin{credit}
I was co-principal investigator and my role was computer modeling of behavioral responses to water scarcity by farmers. I supervised Prof. Hornberger's Ph.D. student John Jacobi for part of his dissertation project which used agent-based modeling of farmer behavior.
\end{credit}
    %
	\item Office of Naval Research ONR-MURI-N00014-11-1-0683 ``Environmental stress and human migration in a low-lying developing nation: A comparison of co-evolving natural and human landscapes in the physically and culturally diverse context of Bangladesh,'' June 2011--May 2016; no-cost extention through May 2017. Total funds \$7.50 million (direct costs\$5.55 million, indirect costs \$1.95 million). Principal Investigator Steven Goodbred (VU EES).
\begin{credit}
I am one of three co-principal investigators (with Prof. Goodbred and Prof. Brooke Ackerly, Political Science) who share leadership of the project. From June--December~2011 I served as acting project leader while Prof.~Goodbred was on leave. The project has three major components: physical science, social science, and integrative science. I am the leader of the integrative science team.
\end{credit}
	%
	\item National Science Foundation: NSF-EAR 1204685, ``Climate, Drought, and Agricultural Adaptations: An Investigation of Vulnerabilities and Responses to Water Stress Among Paddy Farmers in Sri Lanka'' Sept. 2012--Aug. 2017. Total funds: \$3.7 million (direct costs: \$2.4 million, indirect costs: \$1.3 million). Principal Investigator George Hornberger.
\begin{credit}
I was a co-principal investigator and my role in the project is integration of physical and social science through statistical analysis, analysis of satellite remote sensing imagery, and computer modeling of social networks and interaction between behavior and environmental stress as communities of farmers in Sri Lanka adapt to drought and other climatic change.
\end{credit}
\end{enumerate}
\iffalse
\subsubsection{Under Review}
\begin{enumerate}
	\iffalse
    \item ``CNH2-L: Participatory Modeling to Facilitate Understanding, Deliberation, and Decision-Making around Flood Hazards,'' Proposal to Dynamics of Coupled Natural-Human Systems program. Sept.~1, 2019--Aug.~31, 2023. Requested funds: \$1,344,496. Principal Investigator, Jonathan Gilligan. Submitted Feb.~14, 2019. Under review.
    \item ``Quality and Quantity: A Socio-Hydrological Perspective on Water Security,'' NSF Hydrologic Sciences. \emph{Under review}. Total funds: \$795,086 over three years. Direct costs: \$515,275. Indirect costs: \$279,811.
    \item ``Data Science for Everyone,'' Vanderbilt TIPS VIA pre-proposal. \emph{Under review}. Total funds: \$177,046. PI: J.M. Gilligan; Co-PI's: J.B. Ruhl (Law), M. Cohen (Owen), H. Craiglow (Libraries), O. Molvig (History/VIDL); M. Casad (Cinema \& Digital Humanities); G. Narasimham (VIDL).
    \item ``Vanderbilt Institute for Smart Communities Research,'' TIPS VRA pre-proposal. \emph{Under review}. PI: G. Biswas. Co-PIs: H. Baroud, A. Dubey, M. Ellingham, J. Gilligan, D. Kosson, X. Koutsoukos, C. Philip, C. Smrekar, P. Speer, Y. Vorobeychik. Total funds: \$3 million.
    \fi
    \iffalse
    \item ``Connecting Food, Energy, and Water Across Scales and Disciplines,'' NSF NRT-INFEWS. Direct costs: \$2,282,012; indirect costs: \$711,068. \emph{Under review}. Principal Investigator George Hornberger. I am co-principal investigator.
    \fi
    %
    \iffalse
    \item ``Smart and Connected Communities for All: Data-Driven Modeling to Study the Interactions between Public Transit and Housing for Vulnerable Populations,'' NSF EAGER. Direct costs: \$201,598. Indirect costs: \$94,938. \emph{Under review}. Principal Investigator Jonathan Gilligan.
    \item ``NRT: Sustainability Transitions in Coupled Human-Natural Systems - A New Approach for Research and Education on Complex Environmental Systems,''
    NSF NRT, Steven Goodbred (Vanderbilt) Principal Investigator.
    Total funds: \$2,998,911 (direct costs: \$2,560,039; indirect costs: \$438,872). \emph{Under review}.
    %
    \item ``GENSTEM-S: GENeration Z STEM Education through Sustainability,''
    NSF SBIR, Bill Giles (Yonder Systems, Inc.), Principal Investigator.
    Vanderbilt Portion: \$100,218.
    \emph{Under review}.
    %
    \item ``Midwest Energy, Climate, Water Resources, Energy, and Transportation Consortium,'' NOAA RISA. \emph{Under review}. Principal Investigator, Rezaul Mahmood. Vanderbilt lead, Janey Camp.
    %
    \fi

\end{enumerate}%
\fi
