\begin{description}
\item[2024] American Geophysical Union Voices of Science Award.
\item[2023--2024] Fulbright Scholar Award, supporting a sabbatical leave as
  Fulbright Canada Research Chair in Digital Technologies and Sustainability
  at the University of Calgary.
\item[2023] The Margaret Cuninggim Women's Center mentorship award, recognizing
  my mentorship, support, and advocacy for women at Vanderbilt, especially in
  STEM. Vanderbilt University.
\item[2023] Outstanding Reviewer Award, Winter Simulation Conference,
  recognizing the top 2~percent of reviewers, who go above and beyond to provide
  exceptionally thorough, rigorous, and insightful reviews of invited and
  submitted conference papers.
\item[2022] The Alexander Heard Distinguished Service Professor Award,
  Vanderbilt University, recognizing distinctive contributions to the
  understanding of problems of contemporary society.
  (\$5000 cash prize)
\item[2021] Outstanding Reviewer Award, Winter Simulation Conference.
\item[2018] The Chancellor's Award for Research, Vanderbilt University,
  recognizing ``excellence on the part of faculty for
  published research, scholarship or creative expression'' published in the
  previous three years.
  (\$2000 cash prize)
\item[2017] The Morrison Prize for the highest impact paper published in
  2015--2016 on sustainability law and policy (shared with Michael Vandenbergh).
  Sandra Day O'Connor School of Law, Arizona State University.
  (\$10,000 cash prize divided equally between Vandenbergh and myself)
\item[1998] Outstanding Scientific Paper Award, NOAA Environmental Research
  Labs.
\item[1995] NASA Group Achievement Award for outstanding accomplishments and
  contributions to the Airborne Southern Hemisphere Ozone Experiment and
  Measurements to Assess the Effects of Stratospheric Aircraft.
\item[1991--1993] National Research Council Postdoctoral Associate
\item[1985--1986] J.W. Gibbs Fellow, Yale University
%\item[1982] B.A. with Honors, Swarthmore College.
\end{description}
