%
% !TeX root = jmg_cv.tex
%
\begin{rubric}{Invited Talks}%
\entry*[2015]``Understanding Drought and Decision-Making,'' Workshop on Agricultural Drought and Policy, American Institute for Sri Lankan Studies, Colombo, Sri Lanka, March~10.
\entry*[2014]``Land Use, Livelihoods, Vulnerabilities, and Resilience in Coastal Bangladesh,'' in Session PA010: Livelihoods and Ecosystem Services in Vulnerable Delta Regions: Implications for Policy and Practice, American Geophysical Union Fall Meeting, San Francisco~CA, December.
\entry*[2014]``In the Tide Country: Live on an Active Delta in Bangladesh,'' Department of Geography, University of Georgia, October~20.
\entry*[2014]``Integrating Natural and Social Science to Inform Adaptation to Extreme Weather in Bangladesh and Sri Lanka,'' Symposium on Extreme Weather, Disasters and Indigenous Practices in South Asia, Annual Conference on South Asia, Madison~WI October~16.
\entry*[2013]``Integrating Social and Natural Science to Understand Vulnerability and Resilience in Coastal Environments,'' Symposium on Climate Change, Drought, and Agricultural Adaptation, Colombo Sri Lanka, June~7.
\entry*[2013]``Climate Change and Disaster Management,'' Ministry of Disaster Management, Colombo, Sri Lanka, June~5.
\entry*[2012]``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Global Climate Change'' Nashville State Community College, Nashville TN, Mar.~30.
\entry*[2011]``Don't Raise the Bridge, Lower the River: Geoengineering Technology and Governance'' Environmental Governance at the Leading Edge of Technology Conference, George Washington U., Washington DC, Mar.~23.
\entry*[2010]``The Behavioral Wedge: Reducing Greenhouse Gas Emissions by Individuals and Households,'' Joint Statistical Meetings (American Statistical Association, Statistical Society of Canada, etc.), Vancover BC, Aug.~1, 2010. {\bfseries\scshape Note:} Part of a special session to highlight the best papers published in the journal \textit{Significance\/} during the previous year.
\entry*[2009]Panelist, Pew Charitable Trusts Forum on the Law of the Sea Treaty, Belmont University, Nashville TN, Nov.~18.
\entry*[2009]``Global Climate Change: Earth Science, Behavioral Science, and Public Policy," Middle Tennessee State University, Murfreesboro TN, Oct.~16.
\entry*[2009]``From the Laboratory to the Legislature: Why Climate Change is Fundamentally a Transdisciplinary Issue,'' Belmont University, Nashville TN, Feb.~6.
\entry*[2008]``Individual Behavior and Climate Change: The Low-Hanging Fruit,'' Keynote Address, Summit for a Sustainable Tennessee, David Lipscomb University, Nashville TN, Nov.~13.
\entry*[2008]``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Environmental Science and Policy,'' Distinguished Panel Speaker, 10\textsuperscript{th} Beckman Scholars Symposium, Irvine CA, Jul.~26.
\entry*[2008]``Spirituality, Ethics, and the Environment,'' The Kenan Writers' Encounters: Writers and Artists Engage the Environment, Thomas S. Kenan Institute for the Arts \& North Carolina School of the Arts, Winston-Salem NC, Apr.~12.
\entry*[2008]``Ethics in Geological Time: Should We Care about Distant Future Generations?,'' The Berry Lecture, Dept. of Philosophy, Vanderbilt University, Nashville TN, Mar.~24.
\entry*[2007]``Individual Behavior and Greenhouse Gas Emissions,'' Behavior, Energy, and Climate Change conference, 
American Council for an Energy Efficient Economy, Sacramento CA, Nov.~7--9.
\entry*[2006]``Flexibility, Clarity, and Legitimacy: Considerations for Managing Nanotechnology Risks,'' Nanotechnology Governance: Environmental Management from a Global Perspective, Environmental Law Institute and Vanderbilt Center for Environmental Management Studies, Nashville TN, May 19.
\entry*[1998\phantom{--1998}]``\emph{Et in Arcadia Ego}: Reflections on the Future of Tenure,'' Symposium on Promoting Scientific Freedom and Responsibility,
AAAS Annual Meeting, Philadelphia PA.
\entry*[1997]``Smart Modification of Surfaces with Free-Electron Lasers,'' ASM Materials Week '97, Indianapolis IN.
\entry*[1996]``Modification of Diamond Films using Free-Electron Lasers,'' ASM Materials Week '96, Cincinnatti OH.
\entry*[1992]``Quantum Mechanical Measurements with Single Atoms,'' April Meeting of the American Physical Society, Washington DC.
\end{rubric}
