%
% !TeX root = Gilligan_CV.tex
%
\item ``Climate Change in Bangladesh:L A Coupled Natural-Human Systems
   Approach,'' Invited talk, Howard H. Baker, Jr. Center for Public Policy,
   University of Tennessee Knoxville. October 14, 2021.
\item ``Integrating Machine Learning with Agent-Based Modeling to Understand
  Human Impacts of Climate Change.'' Invited seminar, Florida International
  University. May 25, 2021.
\item ``Beyond Politics: The Private Governance Response to Climate
  Change,'' Grand Rounds lecture in Radiology, Vanderbilt Medical Center.
  March 29, 2021.
\item ``New Directions for Climate Policy in an Age of Political Gridlock,``
  Invited colloquium, co-delivered with Michael P. Vandenbergh. Lehigh
  University Department of Environmental Science. October 30, 2020.
\item ``Accounting for Human Behavior in Models of Coupled Natural \& Human
  Systems,'' Invited presentation at Workshop on Coastal Observation and
  Modeling Systems, sponsored by NSF Coastlines and People program. Virtual
  conference hosted by Florida International University, Miami, FL,
  September 8, 2020. (98 attendees).
\item ``Managing Sediment for Sustainability,'' Invited virtual seminar,
  International Centre for Climate Change and Development, Dhaka, Bangladesh,
  July 20, 2020.
\item ``Beyond Wickedness: Managing Complex Systems and Climate Change,''
  Invited presentation, co-delivered with Michael P. Vandenbergh. Vanderbilt
  University Law Review Symposium on Governing Wicked Problems. Nashville, TN,
  October 25, 2019.
\item ``The New Revolving Door," Invited presentation, co-delivered with
  Michael P. Vandenbergh. Case-Western Reserve Law School Symposium on Fifty
  Years of the Environmental Protection Agency. Cleveland, OH, October 18, 2019.
\item ``Agent-Based Modeling of Community Resilience and Environmental
 Non-Migration,'' Invited presentation, First International Conference on
 Environmental Non-Migration: Framework, Methods, and Cases, Technical
 University of Dresden, June 19-21 2019.
\item ``Sediment Management and Sea-Level Rise,'' invited presentation, Fifth
  Annual Gobeshona International Conference on Climate Knowledge, International
  Centre for Climate Change and Development, Dhaka, Bangladesh, January 9, 2019.
\item Invited panelist, ``What Can an Individual Do to Help Limit Climate
  Change,'' public panel discussion at Copenhagen Business School, Aug. 29,
  2018.
\item Invited participant, Workshop on Household Actions to Reduce Greenhouse
  Gas Emissions, Copenhagen Business School, Copenhagen Denmark, August 27--28
  2018 (Host paid for travel, lodging, and meals).
% \item International Symposium on Society and Resource Management (ISSRM), Salt Lake City, UT, June 17--21 2018.
\item Invited panelist, ``Re-envisioning `Sustainable' Deltas through Critical
  Geography,'' American Association of Geographers Annual Conference, April
  2018.
\item ``Carrot and Sticks in Private Climate Governance,'' invited
  presentation, Joint Conference on Environmental Regulation. The Hagler
  Institute for Advanced Study at the Texas A\&M University School of Law and
  the Classical Liberal Institute at the New York University School of Law.
  March 9--10, 2018. (Host paid for travel, lodging, and meals).
\item ``Private Governance Approaches to Climate Policy: Pragmatic Responses to
  Government Inaction,'' Department colloquium, Department of Environmental
  Studies, University of Colorado, Boulder, February~7, 2018 (Host covered
  travel, lodging, meals).
\item ``Energy and the Economy of Sri Lanka,'' invited presentation, Workshop
  on Assessing Stakeholder Preferences in Planning of Energy Sector in Sri
  Lanka, Colombo, Sri Lanka, August~11, 2017.
\item ``Understanding and Adapting to Water Scarcity at the Community Level,''
  invited keynote presentation, Conference on Recognizing Climate Change Risk
  of Dry Zone Farmers, Ministry of Disaster Management, Colombo, Sri Lanka,
  August~10, 2017.
\item ``Planning for Environmental Stress and Disasters: The Importance of
  Interdisciplinary Approaches,'' invited presentation to the Institute of Town
  Planners of Sri Lanka and the Organization of Professional Associations of
  Sri Lanka. Colombo, Sri Lanka, August~9, 2017.
\item ``Quantifying the Potential for Greenhouse Gas Emissions Reductions
  through Private Governance,'' invited presentation to National Academies
  Board on Environmental Change and Society. National Academies, Washington,
  DC, July 11, 2017. (Host covered travel, lodging, \& meals).
\item  ``Connecting Human and Natural Systems: The Role of Agent-Based
  Simulations,'' invited keynote talk, CSDMS 2017 Annual Meeting on Modeling
  Coupled Earth and Human Systems. Boulder, CO. May 23--25 2017. (Host covered
  travel, lodging, meals, \& conference registration). My talk is online at
  \url{https://www.youtube.com/watch?v=v6i5_P_OOcU}.
\item  ``Dynamics of Individual and Collective Agricultural Adaptation to Water
  Security,'' invited talk, Winter Simulation Conference 2016, Arlington, VA,
  December~12, 2016.
\item ``Understanding Drought and Decision-Making,'' Workshop on Agricultural
  Drought and Policy, American Institute for Sri Lankan Studies, Colombo, Sri
  Lanka, March~10, 2015.
\item ``Land Use, Livelihoods, Vulnerabilities, and Resilience in Coastal
  Bangladesh,'' in Session PA010: Livelihoods and Ecosystem Services in
  Vulnerable Delta Regions: Implications for Policy and Practice, American
  Geophysical Union Fall Meeting, San Francisco~CA, December~2014.
\item ``In the Tide Country: Live on an Active Delta in Bangladesh,''
  Department of Geography, University of Georgia, October~20, 2014 (Host
  covered travel, lodging, \& meals).
\item ``Integrating Natural and Social Science to Inform Adaptation to Extreme
  Weather in Bangladesh and Sri Lanka,'' Symposium on Extreme Weather,
  Disasters and Indigenous Practices in South Asia, Annual Conference on South
  Asia, Madison~WI October~16, 2014 (American Institute of Sri Lanka Studies
  covered conference registration and 50\% of travel \& lodging).
