%
% !TeX root = Gilligan_CV.tex
%
\item ``Integrating Social and Natural Science to Understand Vulnerability and Resilience in Coastal Environments,'' Symposium on Climate Change, Drought, and Agricultural Adaptation, Colombo, Sri Lanka, June~7, 2013.
\item ``Climate Change and Disaster Management,'' Ministry of Disaster Management, Colombo, Sri Lanka, June~5, 2013.
\item ``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Global Climate Change'' Nashville State Community College, Nashville TN, March~30, 2012.
\item ``Don't Raise the Bridge, Lower the River: Geoengineering Technology and Governance'' Environmental Governance at the Leading Edge of Technology Conference, George Washington U., Washington DC, March~23, 2011 (Host covered travel, lodging \& conference registration).
\item ``The Behavioral Wedge: Reducing Greenhouse Gas Emissions by Individuals and Households,'' Joint Statistical Meetings (American Statistical Association, Statistical Society of Canada, etc.), Vancover BC, August~1, 2010. {\bfseries\scshape Note:} Part of a special session to highlight the best papers published in the journal \textit{Significance\/} during the previous year. (Host covered travel, lodging, \& conference registration).
\item Panelist, Pew Charitable Trusts Forum on the Law of the Sea Treaty, Belmont University, Nashville TN, November~18, 2009.
\item ``Global Climate Change: Earth Science, Behavioral Science, and Public Policy," Middle Tennessee State University, Murfreesboro TN, October~16, 2009.
\item ``From the Laboratory to the Legislature: Why Climate Change is Fundamentally a Transdisciplinary Issue,'' Belmont University, Nashville TN, February~6, 2009 (Host paid honorarium)
\item ``Individual Behavior and Climate Change: The Low-Hanging Fruit,'' Keynote Address, Summit for a Sustainable Tennessee, David Lipscomb University, Nashville TN, November~13, 2008.
\item ``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Environmental Science and Policy,'' Distinguished Panel Speaker, 10\textsuperscript{th} Beckman Scholars Symposium, Irvine CA, July~26, 2008. (Host covered travel \& lodging and paid an honorarium).
\item ``Spirituality, Ethics, and the Environment,'' The Kenan Writers' Encounters: Writers and Artists Engage the Environment, Thomas S. Kenan Institute for the Arts \& North Carolina School of the Arts, Winston-Salem NC, April~12, 2008. (Host covered travel, lodging, and paid an honorarium).
\item ``Ethics in Geological Time: Should We Care about Distant Future Generations?,'' The Berry Lecture, Dept. of Philosophy, Vanderbilt University, Nashville TN, March~24, 2008 (honorarium).
\item ``Individual Behavior and Greenhouse Gas Emissions,'' Behavior, Energy, and Climate Change conference, American Council for an Energy Efficient Economy, Sacramento CA, November~7--9, 2007
\item ``Flexibility, Clarity, and Legitimacy: Considerations for Managing Nanotechnology Risks,'' Nanotechnology Governance: Environmental Management from a Global Perspective, Environmental Law Institute and Vanderbilt Center for Environmental Management Studies, Nashville TN, May 19, 2006.
\item ``\emph{Et in Arcadia Ego}: Reflections on the Future of Tenure,'' Symposium on Promoting Scientific Freedom and Responsibility, AAAS Annual Meeting, Philadelphia PA (1998).
\item ``Smart Modification of Surfaces with Free-Electron Lasers,'' ASM Materials Week '97, Indianapolis IN (1997).
\item ``Modification of Diamond Films using Free-Electron Lasers,'' ASM Materials Week '96, Cincinnatti OH (1996).
\item ``Quantum Mechanical Measurements with Single Atoms,'' April Meeting of the American Physical Society, Washington DC (1992).
