%
% !TeX root = Gilligan_CV.tex
%
\subsubsection{Tenure-Track}
\emph{The following talks were given while on tenure-track}
\begin{enumerate}
\item ``Agent-Based Modeling of Community Resilience and Environmental Non-Migration,'' Invited presentation, Conference on Environmental Non-Migration: Framework, Methods, and Cases, Technical University of Dresden, June 19-21 2019.
\item ``Sediment Management and Sea-Level Rise,'' inited presentation, Fifth Annual Gobeshona International Conference on Climate Knowledge, International Centre for Climate Change and Development, Dhaka, Bangladesh, January 9, 2019.
\item Invited panelist, ``What Can an Individual Do to Help Limit Climate Change,'' public panel discussion at Copenhagen Business School, Aug. 29, 2018.
\item Invited participant, Workshop on Household Actions to Reduce Greenhouse Gas Emissions, Copenhagen Business School, Copenhagen Denmark, August 27--28 2018 (Host paid for travel, lodging, and meals).
% \item International Symposium on Society and Resource Management (ISSRM), Salt Lake City, UT, June 17--21 2018.
\item Panel on ``Re-envisioning `sustainable' deltas through critical geography,'' American Association of Geographers Annual Conference, April 2018.
\item ``Carrot and Sticks in Private Climate Governance,'' invited presentation, Joint Conference on Environmental Regulation. The Hagler Institute for Advanced Study at the Texas A\&M University School of Law and the Classical Liberal Institute at the New York University School of Law. March 9--10, 2018. (Host paid for travel, lodging, and meals).
\item ``Private Governance Approaches to Climate Policy: Pragmatic Responses to Government Inaction,'' Department colloquium, Department of Environmental Studies, University of Colorado, Boulder, February~7, 2018 (Host will cover travel, lodging, meals).
\item ``Energy and the Economy of Sri Lanka,'' invited presentation, Workshop on Assessing Stakeholder Preferences in Planning of Energy Sector in Sri Lanka, Colombo, Sri Lanka, August~11, 2017.
\item ``Understanding and Adapting to Water Scarcity at the Community Level,'' invited keynote presentation, Conference on Recognizing Climate Change Risk of Dry Zone Farmers, Ministry of Disaster Management, Colombo, Sri Lanka, August~10, 2017.
\item ``Planning for Environmental Stress and Disasters: The Importance of Interdisciplinary Approaches,'' invited presentation to the Institute of Town Planners of Sri Lanka and the Organization of Professional Associations of Sri Lanka. Colombo, Sri Lanka, August~9, 2017.
\item ``Quantifying the Potential for Greenhouse Gas Emissions Reductions through Private Governance,'' invited presentation to National Academies Board on Environmental Change and Society. National Academies, Washington, DC, July 11, 2017. (Host covered travel, lodging, \& meals).
\item  ``Connecting Human and Natural Systems: The Role of Agent-Based Simulations,'' invited keynote talk, CSDMS 2017 Annual Meeting on Modeling Coupled Earth and Human Systems. Boulder, CO. May 23--25 2017. (Host covered travel, lodging, meals, \& conference registration). My talk is online at \url{https://www.youtube.com/watch?v=v6i5_P_OOcU}.
\item  ``Dynamics of Individual and Collective Agricultural Adaptation to Water Security,'' invited talk, Winter Simulation Conference 2016, Arlington, VA, December~12, 2016.
\item ``Understanding Drought and Decision-Making,'' Workshop on Agricultural Drought and Policy, American Institute for Sri Lankan Studies, Colombo, Sri Lanka, March~10, 2015.
\end{enumerate}

\subsubsection{Pre-Tenure Track}
\emph{The following talks were given pre-tenure-track}
\begin{enumerate}
\item ``Land Use, Livelihoods, Vulnerabilities, and Resilience in Coastal Bangladesh,'' in Session PA010: Livelihoods and Ecosystem Services in Vulnerable Delta Regions: Implications for Policy and Practice, American Geophysical Union Fall Meeting, San Francisco~CA, December~2014.
\item ``In the Tide Country: Live on an Active Delta in Bangladesh,'' Department of Geography, University of Georgia, October~20, 2014 (Host covered travel, lodging, \& meals).
\item ``Integrating Natural and Social Science to Inform Adaptation to Extreme Weather in Bangladesh and Sri Lanka,'' Symposium on Extreme Weather, Disasters and Indigenous Practices in South Asia, Annual Conference on South Asia, Madison~WI October~16, 2014 (American Institute of Sri Lanka Studies covered conference registration and 50\% of travel \& lodging).
\item ``Integrating Social and Natural Science to Understand Vulnerability and Resilience in Coastal Environments,'' Symposium on Climate Change, Drought, and Agricultural Adaptation, Colombo, Sri Lanka, June~7, 2013.
\item ``Climate Change and Disaster Management,'' Ministry of Disaster Management, Colombo, Sri Lanka, June~5, 2013.
\item ``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Global Climate Change'' Nashville State Community College, Nashville TN, March~30, 2012.
\item ``Don't Raise the Bridge, Lower the River: Geoengineering Technology and Governance'' Environmental Governance at the Leading Edge of Technology Conference, George Washington U., Washington DC, March~23, 2011 (Host covered travel, lodging \& conference registration).
\item ``The Behavioral Wedge: Reducing Greenhouse Gas Emissions by Individuals and Households,'' Joint Statistical Meetings (American Statistical Association, Statistical Society of Canada, etc.), Vancover BC, August~1, 2010. {\bfseries\scshape Note:} Part of a special session to highlight the best papers published in the journal \textit{Significance\/} during the previous year. (Host covered travel, lodging, \& conference registration).
\item Panelist, Pew Charitable Trusts Forum on the Law of the Sea Treaty, Belmont University, Nashville TN, November~18, 2009.
\item ``Global Climate Change: Earth Science, Behavioral Science, and Public Policy," Middle Tennessee State University, Murfreesboro TN, October~16, 2009.
\item ``From the Laboratory to the Legislature: Why Climate Change is Fundamentally a Transdisciplinary Issue,'' Belmont University, Nashville TN, February~6, 2009 (Host paid honorarium)
\item ``Individual Behavior and Climate Change: The Low-Hanging Fruit,'' Keynote Address, Summit for a Sustainable Tennessee, David Lipscomb University, Nashville TN, November~13, 2008.
\item ``From the Laboratory to the Legislature: Transdisciplinary Perspectives on Environmental Science and Policy,'' Distinguished Panel Speaker, 10\textsuperscript{th} Beckman Scholars Symposium, Irvine CA, July~26, 2008. (Host covered travel \& lodging and paid an honorarium).
\item ``Spirituality, Ethics, and the Environment,'' The Kenan Writers' Encounters: Writers and Artists Engage the Environment, Thomas S. Kenan Institute for the Arts \& North Carolina School of the Arts, Winston-Salem NC, April~12, 2008. (Host covered travel, lodging, and paid an honorarium).
\item ``Ethics in Geological Time: Should We Care about Distant Future Generations?,'' The Berry Lecture, Dept. of Philosophy, Vanderbilt University, Nashville TN, March~24, 2008 (honorarium).
\item ``Individual Behavior and Greenhouse Gas Emissions,'' Behavior, Energy, and Climate Change conference, American Council for an Energy Efficient Economy, Sacramento CA, November~7--9, 2007
\item ``Flexibility, Clarity, and Legitimacy: Considerations for Managing Nanotechnology Risks,'' Nanotechnology Governance: Environmental Management from a Global Perspective, Environmental Law Institute and Vanderbilt Center for Environmental Management Studies, Nashville TN, May 19, 2006.
\item ``\emph{Et in Arcadia Ego}: Reflections on the Future of Tenure,'' Symposium on Promoting Scientific Freedom and Responsibility, AAAS Annual Meeting, Philadelphia PA (1998).
\item ``Smart Modification of Surfaces with Free-Electron Lasers,'' ASM Materials Week '97, Indianapolis IN (1997).
\item ``Modification of Diamond Films using Free-Electron Lasers,'' ASM Materials Week '96, Cincinnatti OH (1996).
\item ``Quantum Mechanical Measurements with Single Atoms,'' April Meeting of the American Physical Society, Washington DC (1992).
\end{enumerate}
