%
% !TeX root = Gilligan_CV_2015.tex
%
\begin{enumerate}
%
	  \item 
	  \textdagger \enquote{Data-Driven Dynamic Decision Models}, 
	  by *J.J. Nay, and \textbf{J.M. Gilligan},
	  in Proc.\ 2015 Winter Simulation Conf., L. Yilmaz, W.K.V. Chan, I. Moon, T.M.K. Roeder, C. Macal, and M. Rosetti (eds.). 12~pp. (2015). \url{http://dl.acm.org/citation.cfm?id=2888935}
	  \begin{credit}
	  My student, Nay, came up with the idea, gathered the data, and did most of the programming. I introduced the idea of representing strategies as finite-state machines and using genetic algorithms to find the optimal strategy in order to implement his idea. We both contributed equally to writing the paper.
	  \end{credit}
%
	  \item 
	  \textdagger \enquote{Participatory Simulations of Urban Flooding for Learning and Decision Support}, 
	  by \textbf{J.M. Gilligan}, Corey Brady, Janey V. Camp, *J.J. Nay, and Pratim Sengupta.
	  in Proc.\ 2015 Winter Simulation Conf., L. Yilmaz, W.K.V. Chan, I. Moon, T.M.K. Roeder, C. Macal, and M. Rosetti (eds.). 2~pp. (2015). \url{http://dl.acm.org/citation.cfm?id=2889027}
	  \begin{credit}
	  The concept and design originated in equal parts from myself, Camp, and Sengupta. Brady and Nay did the programming. Brady and Sengupta conducted the human-subject experiments. I wrote the paper.
	  \end{credit}
%
	  \item 
	  \enquote{Farming Practices and Anthropogenic Delta Dynamics}, 
	  by K.G. Rogers, J.P.M. Syvitski, I. Overeem, S. Higgins, and \textbf{J.M. Gilligan},
	  in \emph{Deltas: Landforms, Ecosystems and Human Activities,} Proc.\ Int'l. Assoc.\ Hydrolog.\ Sci., Gothenberg SE, July 2013 (IAHS Publ.\ 358, 2013), pp.~133--142.
	  \begin{credit}
	  I contributed the analysis of strong coupling between human and natural systems and historical perspective of management and mismanagement of sediment transport and flooding in Bangladesh since the 1920s.
	  \end{credit}
%
	\item
	\enquote{Building Resilience to Environmental Stress in Coastal Bangladesh: An Integrated Social, Environmental, and Engineering Perspective,} by \textbf{J.M. Gilligan}, B.A. Ackerly, and S.L. Goodbred, Jr., peer reviewed paper presented at "Bridging the Policy-Action Divide: Challenges and Prospects for Bangladesh," Bangladesh Development Initiative (Berkeley CA, Feb. 22-24, 2013).
	\begin{credit}
	The three authors contributed equally to the major ideas and I wrote the entire paper.
	\end{credit}
	\item
	\enquote{Laser-induced alterations of the infrared light absorption by biological tissues: radiometric and spectroscopic measurements,}  by E.~Sobol, A.P.~Sviridov, M.S.~Kitai, V.N. Bagratashvili, \textbf{J.~M. Gilligan}, and G.~S. Edwards, in
	  Proc.~SPIE \textbf{4829}, 1030--1031 (2000). 
	  \begin{credit}
	  I contributed significantly to designing and performing the experiments, analyzing the data, and writing the paper. My contribution to the experiments included designing and performing the laser irradiation and performing FTIR spectroscopy on the samples before and after irradiation.
	  \end{credit}
	%
	\item
	\enquote{Infrared free-electron laser photoablation of diamond films,} by *J. Sturmann, *Z. Marka, *M.M. Albert, R.G. Albridge, \textbf{J.M. Gilligan}, G. L\"upke, S.K. Singh, J.L. Davidson, W. Husinsky, and N.H. Tolk,
	Proc.~SPIE \textbf{4423}, 206--211 (2001).
	  \begin{credit}
	  Advances in understanding the mechanisms by which lasers cut through diamond.
	  This was principally Sturmann's work. I contributed to designing and performing the experiments.
	  \end{credit}
	%
	\item
	\enquote{Alteration of absorption coefficients of tissue water as a result of
	  heating under {IR} {FEL} radiation with different wavelengths,}  by E.~Sobol,
	  A.~Sviridov, M.~Kitai, \textbf{J.~M. Gilligan}, and G.~S. Edwards, in
	  \emph{International Biomedical Optics Symposium}, vol. 3925, p.~78 (SPIE,
	  2000). 
	  \begin{credit}
	  I contributed significantly to designing and performing the experiments, analyzing the data, and writing the paper. My contribution to the experiments included designing and performing the laser irradiation and performing FTIR spectroscopy on the samples before and after irradiation.
	  \end{credit}
	%
	\item
	\enquote{Effect of wavelength on threshold and kinetics of tissue denaturation
	  under laser radiation,}  by E.~Sobol, A.~Sviridov, M.~Kitai, , G.~S. Edwards,
	  \textbf{J.~M. Gilligan}, and N.~H. Tolk, in \emph{International Biomedical Optics
	  Symposium}, vol. 3601, pp. 122--9 (SPIE, 1999). 
	  \begin{credit}
	   I contributed significantly to designing and performing the experiments, analyzing the data, and writing the paper. My contribution to the experiments included designing and performing the laser irradiation and performing FTIR spectroscopy on the samples before and after irradiation.
	  \end{credit}
	%
	\item
	\enquote{Light scattered from two atoms,}  by W.~M. Itano, U.~Eichmann, J.~C.
	  Bergquist, J.~J. Bollinger, \textbf{J.~M. Gilligan}, M.~G. Raizen, and D.~J. Wineland,
	  in \emph{Proc.\ 11$^{\mbox{\scriptsize th}}$ Int'l.\ Conf.\ Laser Science},
	  pp. 410--9 (1993). 
	  \begin{credit}
	   This work was principally Eichmann's and Itano's. I invented the Brewster-plate measurement technique that made these experiments possible. I participated significantly in performing the experiments.
	  \end{credit}
	%
	\item
	\enquote{Interference in the resonance fluorescence of two trapped atoms,}  by
	  U.~Eichmann, J.~C. Bergquist, J.~J. Bollinger, \textbf{J.~M. Gilligan}, W.~M. Itano,
	  J.~G. Raizen, and D.~J. Wineland, in \emph{Proc.\ 11$^{\mbox{\scriptsize
	  th}}$ Int'l.\ Conf.\ Laser Science}, pp. 43--8 (1993). 
	  \begin{credit}
	   This work was principally Eichmann's. I invented Brewster-plate technique for switching between measurements that contain quantum ``which-path'' information and measurements that do not and participated significantly in performing the experiments. 
	  \end{credit}
	%
	\item
	\enquote{Recent experiments on trapped ions at the {N}ational {I}nstitute of
	  {S}tandards and {T}echnology,}  by D.~J. Wineland, J.~C. Bergquist, J.~J.
	  Bollinger, W.~M. Itano, F.~L. Moore, \textbf{J.~M. Gilligan}, M.~G. Raizen, D.~J.
	  Heinzen, C.~S. Weimer, and C.~H. Manney, in \emph{Proc.\ Enrico Fermi Summer
	  School on Laser Manipulation of Atoms and Ions, {J}uly 1991, {V}arenna,
	  {I}taly}, pp. 553--67 (1991). 
	  \begin{credit}
	   This paper was an overview of the entire group's work. I participated in measuring quantum projection noise.
	  \end{credit}
	%
	\item
	\enquote{High-resolution spectroscopy of laser-cooled ions,}  by D.~J.
	  Wineland, J.~C. Bergquist, J.~J. Bollinger, W.~M. Itano, F.~L. Moore, \textbf{J.~M.
	  Gilligan}, M.~G. Raizen, D.~J. Heinzen, C.~S. Weimer, and C.~H. Manney, in
	  \emph{Proc.\ Enrico Fermi Summer School on Laser Manipulation of Atoms and
	  Ions, {J}uly 1991, {V}arenna, {I}taly}, pp. 539--51 (1991). 
	  \begin{credit}
	   This paper was an overview of the entire group's work. I performed high-resolution spectroscopic measurements of hyperfine splitting in magnesium ions.
	  \end{credit}
	%
	\item
	\enquote{Precise multiphoton spectroscopy of {H$_2$},}  by E.~E. Eyler, \textbf{J.~M.
	  Gilligan}, and E.~McCormack, in \emph{Advances in Laser Spectroscopy III},
	  vol. 172 of \emph{AIP Conference Proceedings}, pp. 331--3 (1988). 
	  \begin{credit}
	   McCormack and I (both graduate students) contributed equally to performing the experiments and analyzing data. Eyler was our advisor.
	  \end{credit}
	%
	\item
	\enquote{Precise photodissociation and multiphoton spectroscopy of {H$_2$},}
	  by E.~McCormack, E.~E. Eyler, and \textbf{J.~M. Gilligan}, in \emph{XV Int'l Conf.\
	  Quantum Electronics}, vol.~21 of \emph{Technical Digest Series}, pp. 58--60
	  (Optical Society of America, 1987). 
	  \begin{credit}
	   This was primarily McCormack's work. I made significant contributions to performing the experiments and preliminary data analysis.
	  \end{credit}
	%
	\item
	\enquote{Precise multiphoton spectroscopy of excited states of {H$_2$},}  by
	  E.~E. Eyler and \textbf{J.~M. Gilligan}, in \emph{Advances in Laser Spectroscopy II},
	  vol. 160 of \emph{AIP Conference Proceedings}, pp. 388--90 (1987). 
	  \begin{credit}
	   I designed and built apparatus and performed the measurements. Eyler and I contributed equally to analyzing data an interpreting the results.
	  \end{credit}
	%
\end{enumerate}
