%
% !TeX root = Gilligan_CV_2015.tex
%
\begin{enumerate}
%
    \item
    \textdagger\
    *E. Burchfield, *J.J. Nay, and \textbf{J. Gilligan},
    \enquote{Application of Machine Learning to the Prediction of Vegetation Health},
    International Archives of Photogrammatry, Remote Sensing, and Spatial Informatioon Science \textbf{XLI-B2}, 465--469 (2016).
%
    \item
    \textdagger\
    *E.K. Burchfield, and \textbf{J. Gilligan},
    \enquote{Dynamics of Individual and Collective Agricultural Adaptation to Water Scarcity,}
    Proc.\ 2016 Winter Simulation Conf., T.M.K. Roeder, P.I. Frazier, R. Szechtman, E. Zhou, T. Huschka, and S.E. Chick (eds.).
    (2016), pp.~1678--89.
%
    \item
    \textdagger\
    *J.J. Nay, *M. Van der Linden, and \textbf{J.M. Gilligan},
    \enquote{Betting and Belief: Prediction Markets and Attribution of Climate Change,}
    Proc.\ 2016 Winter Simulation Conf., T.M.K. Roeder, P.I. Frazier, R. Szechtman, E. Zhou, T. Huschka, and S.E. Chick (eds.).
    (2016), pp.~1666--77.
%
    \item 
    \textdagger\
    *J.J. Nay, and \textbf{J.M. Gilligan},
    \enquote{Data-Driven Dynamic Decision Models}, 
    in Proc.\ 2015 Winter Simulation Conf., L. Yilmaz, W.K.V. Chan, I. Moon, T.M.K. Roeder, C. Macal, and M. Rosetti (eds.). 
      (2015), pp.~2752--63. 
%
    \item 
    \textdagger\
    \textbf{J.M. Gilligan}, Corey Brady, Janey V. Camp, *J.J. Nay, and Pratim Sengupta.
    \enquote{Participatory Simulations of Urban Flooding for Learning and Decision Support}, 
    in Proc.\ 2015 Winter Simulation Conf., L. Yilmaz, W.K.V. Chan, I. Moon, T.M.K. Roeder, C. Macal, and M. Rosetti (eds.). 
      (2015), pp.~3174--75.
%
    \item 
    \textdagger\
    K.G. Rogers, J.P.M. Syvitski, I. Overeem, S. Higgins, and \textbf{J.M. Gilligan},
    \enquote{Farming Practices and Anthropogenic Delta Dynamics}, 
    in \emph{Deltas: Landforms, Ecosystems and Human Activities,} Proc.\ Int'l. Assoc.\ Hydrolog.\ Sci., Gothenberg SE, July 2013 (IAHS Publ.\ 358, 2013), pp.~133--142.
%
    \item
    \textbf{J.M. Gilligan}, B.A. Ackerly, and S.L. Goodbred, Jr., 
    \enquote{Building Resilience to Environmental Stress in Coastal Bangladesh: An Integrated Social, Environmental, and Engineering Perspective,} 
    Bridging the Policy-Action Divide: Challenges and Prospects for Bangladesh," Bangladesh Development Initiative (Berkeley CA, Feb. 22-24, 2013).
%  
    \item
    E.~Sobol, A.P.~Sviridov, M.S.~Kitai, V.N. Bagratashvili, \textbf{J.M. Gilligan}, and G.S. Edwards, 
    \enquote{Laser-induced alterations of the infrared light absorption by biological tissues: radiometric and spectroscopic measurements,}  
    Proc.~SPIE \textbf{4829}, 1030--1031 (2000). 
%
    \item
    *J. Sturmann, *Z. Marka, *M.M. Albert, R.G. Albridge, \textbf{J.M. Gilligan}, G. L\"upke, S.K. Singh, J.L. Davidson, W. Husinsky, and N.H. Tolk,
    \enquote{Infrared free-electron laser photoablation of diamond films,} 
    Proc.~SPIE \textbf{4423}, 206--211 (2001).
%
    \item
    E.~Sobol, A.~Sviridov, M.~Kitai, \textbf{J.M. Gilligan}, and G.S. Edwards,
    \enquote{Alteration of absorption coefficients of tissue water as a result of heating under {IR} {FEL} radiation with different wavelengths,}  
    \emph{International Biomedical Optics Symposium}, vol. 3925, p.~78 (SPIE, 2000). 
%
    \item
    E.~Sobol, A.~Sviridov, M.~Kitai, , G.S. Edwards, \textbf{J.M. Gilligan}, and N.H. Tolk, 
    \enquote{Effect of wavelength on threshold and kinetics of tissue denaturation under laser radiation,}  
      in \emph{International Biomedical Optics Symposium}, vol. 3601, pp. 122--9 (SPIE, 1999). 
%
    \item
    W.M. Itano, U.~Eichmann, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, M.G. Raizen, and D.J. Wineland,
    \enquote{Light scattered from two atoms,}  
    \emph{Proc.\ 11\textsuperscript{th} Int'l.\ Conf.\ Laser Science},
    pp. 410--9 (1993). 
%
    \item
    U.~Eichmann, J.C. Bergquist, J.J. Bollinger, \textbf{J.M. Gilligan}, W.M. Itano, J.G. Raizen, and D.J. Wineland, 
    \enquote{Interference in the resonance fluorescence of two trapped atoms,}
    \emph{Proc.\ 11\textsuperscript{th} Int'l.\ Conf.\ Laser Science}, pp. 43--8 (1993). 
%
    \item
    D.J. Wineland, J.C. Bergquist, J.J. Bollinger, W.M. Itano, F.L. Moore, \textbf{J.M. Gilligan}, M.G. Raizen, D.J. Heinzen, C.S. Weimer, and C.H. Manney, 
    \enquote{Recent experiments on trapped ions at the {N}ational {I}nstitute of {S}tandards and {T}echnology,}  
    \emph{Proc.\ Enrico Fermi Summer School on Laser Manipulation of Atoms and Ions, {J}uly 1991, {V}arenna, {I}taly}, pp. 553--67 (1991). 
%
    \item
    D.J. Wineland, J.C. Bergquist, J.J. Bollinger, W.M. Itano, F.L. Moore, \textbf{J.M. Gilligan}, M.G. Raizen, D.J. Heinzen, *C.S. Weimer, and C.H. Manney,
    \enquote{High-resolution spectroscopy of laser-cooled ions,}  
    \emph{Proc.\ Enrico Fermi Summer School on Laser Manipulation of Atoms and
    Ions, {J}uly 1991, {V}arenna, {I}taly}, pp. 539--51 (1991). 
%
    \item
    E.E. Eyler, \textbf{J.M. Gilligan}, and E.~McCormack, 
    \enquote{Precise multiphoton spectroscopy of {H$_2$},}  
    \emph{Advances in Laser Spectroscopy III}, vol. 172 of \emph{AIP Conference Proceedings}, pp. 331--3 (1988). 
%
    \item
    E.~McCormack, E.E. Eyler, and \textbf{J.M. Gilligan}, 
    \enquote{Precise photodissociation and multiphoton spectroscopy of {H$_2$},}
      \emph{XV Int'l Conf.\ Quantum Electronics}, vol.~21 of \emph{Technical Digest Series}, pp. 58--60 (Optical Society of America, 1987). 
%
    \item
    E.E. Eyler and \textbf{J.M. Gilligan}, 
    \enquote{Precise multiphoton spectroscopy of excited states of {H$_2$},}
    \emph{Advances in Laser Spectroscopy II}, vol. 160 of \emph{AIP Conference Proceedings}, pp. 388--90 (1987). 
%
\end{enumerate}
