\begin{rubric}{Publications}%
"Time-resolved light scattering measurements of cartilage and cornea denaturation due to FEL radiation," by E. Sobol, A. Sviridov, M. Kitai, J.M. Gilligan, G.S. Edwards, and N.H. Tolk, submitted to Biopolymers. 
"Alteration of absorption coefficients of tissue water as a result of heating under IR FEL radiation with different wavelengths," by E. Sobol, A. Sviridov, M. Kitai, J.M. Gilligan, and G.S. Edwards, Proc. SPIE (in press). 
"Effect of wavelength on threshold and kinetics of tissue denaturation under laser radiation," by E. Sobol, A. Sviridov, M. Kitai, G.S. Edwards, J.M. Gilligan, and N.H. Tolk, Proc. SPIE 3601, 122-9 (1999). 
"Chemical contrast observed at a III-V heterostructure by scanning near-field optical microscopy," by A. Cricenti, R. Generosi, G. Herold, P. Chiaradia, P. Perfetti, G. Margaritondo, J.M. Gilligan, and N.H. Tolk, Physica Status Solidi a-Applied Research 175, 345-9 (1999). 
"Interface applications of scanning near-field optical microscopy with a free electron laser," by A. Cricenti, R. Generosi, P. Perfetti, G. Margaritondo, J. Almeida, J.M. Gilligan, N.H. Tolk, C. Coluzza, M. Spajer, D. Courjon, and I.D. Aggarwal, Physica Status Solidi a-Applied Research 175, 317-29 (1999). 
"Nonlinear energy-selective nanoscale modifications of materials and dynamics in metals and semiconductors," by S. Marka, C.P. Cheney, W. Wang, G. Lupke, J. Gilligan, Y. Yao, and N.H. Tolk, Technical Physics 44, 1069-72 (1999). 
"Singlemode chalcogenide fiber infrared SNOM probes," by D.T. Schaafsma, R. Mossadegh, J.S. Sanghera, I.D. Aggarwal, J.M. Gilligan, N.H. Tolk, M. Luce, R. Generosi, P. Perfetti, A. Cricenti, and G. Margaritondo, Ultramicroscopy 77, 77-81 (1999). 
"Fabrication of single-mode chalcogenide fiber probes for scanning near-field infrared optical microscopy," by D.T. Schaafsma, R. Mossadegh, J.S. Sanghera, I.D. Aggarwal, M. Luce, R. Generosi, P. Perfetti, A. Cricenti, J.M. Gilligan, and N.H. Tolk, Opt. Eng. 38, 1381-5 (1999). 
"First experimental results with the free electron laser coupled to a scanning near-field optical microscope," by A. Cricenti, R. Generosi, C. Barchesi, M. Luce, M. Rinaldi, C. Coluzza, P. Perfetti, G. Margaritondo, D.T. Schaafsma, I.D. Aggarwal, J.M. Gilligan, and N.H. Tolk, Physica Status Solidi a-Applied Research 170, 241-7 (1998). 
"Free-electron-laser near-field nanospectroscopy," by A. Cricenti, R. Generosi, P. Perfetti, J.M. Gilligan, N.H. Tolk, C. Coluzza, and G. Margaritondo, Appl. Phys. Lett. 73, 151-3 (1998). 
"Infrared wavelength-selective photodesorption on diamond surfaces," by J. Sturmann, R.G. Albridge, A.V. Barnes, J.L. Davidson, J.M. Gilligan, G. Lupke, A. Ueda, and N.H. Tolk, Appl. Surf. Sci. 129, 59-63 (1998). 
"Molecular effects in measured sputtering yields on gold at near threshold energies," by N.H. Tolk, Z. Hargitai, Y. Yao, B. Pratt-Ferguson, M.M. Albert, R.G. Albridge, A.V. Barnes, J.M. Gilligan, V.D. Gordon, G. Lupke, A. Puckett, J. Tully, G. Betz, and W. Husinsky, Izv. Akad. Nauk. Ser. Fiz. 62, 676-9 (1998). 
"Coupled electron-hole dynamics at the Si/SiO2 interface," by W. Wang, G. Lupke, M. Di Ventra, S.T. Pantelides, J.M. Gilligan, N.H. Tolk, I.C. Kizilyalli, P.K. Roy, G. Margaritondo, and G. Lucovsky, Phys. Rev. Lett. 81, 4224-7 (1998). 
"New molecular collisional interaction effect in low-energy sputtering," by Y. Yao, Z. Hargitai, M. Albert, R.G. Albridge, A.V. Barnes, J.M. Gilligan, B.P. Ferguson, G. Lupke, V.D. Gordon, N.H. Tolk, J.C. Tully, G. Betz, and W. Husinsky, Phys. Rev. Lett. 81, 550-3 (1998). 
"Evaluation of source gas lifetimes from stratospheric observations," by C.M. Volk, J.W. Elkins, D.W. Fahey, G.S. Dutton, J.M. Gilligan, M. Loewenstein, J.R. Podolske, K.R. Chan, and M.R. Gunson, J. Geophys. Res. Atmos. 102, 25543-64 (1997). 
"Photoexcitation Spectroscopy and Material Alteration with Free-Electron Laser," by J. Sturmann, R.G. Albridge, A.V. Barnes, J. Gilligan, M.T. Graham, J.T. McKinley, W. Wang, X. Yang, N.H. Tolk, J.L. Davidson, and G. Margaritondo, Acta Physica Polonica A 91, 689-96 (1997). 
"Quantifying Transport Between the Tropical and Mid-Latitude Lower Stratosphere," by C. M. Volk, J. W. Elkins, D./ W. Fahey, R. J. Salawitch, G. S. Dutton, J. M. Gilligan, M. H. Proffitt, M. Loewenstein, J. R. Podolske, K. Minschwaner, J. J. Margitan, and K. R. Chan, Science 272, 1763-8 (1996). 
"Airborne gas chromatograph for in situ measurements of long-lived species in the upper troposphere and lower stratosphere," by J. W. Elkins, D. W. Fahey, J. M. Gilligan, G. S. Dutton, T. J. Baring, C. M. Volk, R. E. Dunn, R. C. Myers, S. A. Montzka, P. R. Wamsley, A. H. Hayden, J. H. Butler, T. M. Thompson, T. H. Swanson, E. J. Dlugokencky, P. C. Novelli, D. F. Hurst, J. M. Lobert, S. J. Ciciora, R. J. McLaughlin, T. L. Thompson, R. H. Winkler, P. J. Fraser, L. P. Steele, and M. P. Lucarelli, Geophys. Res. Lett. 23, 347-50 (1996). 
"Estimates of total organic and inorganic chlorine in the lower stratosphere from in situ measurements during aase ii," by E. L. Woodbridge, J. W. Elkins, D. W. Fahey, L. E. Heidt, S. Solomon, T. J. Baring, T. J. Gilpin, W. H. Pollock, S. M. Schauffler, E. L. Atlas, M. Lowenstein, J. R. Podolske, C. R. Webster, R. D. May, J. M. Gilligan, S. A. Montzka, K. A. Boering, and R. J. Salawitch, J. Geophys. Res. 100, 3057-64 (1995). 
"Refinement of the total organic and inorganic chlorine budgets in the atmosphere with a new in situ instrument, Airborne Chromatograph for Atmospheric Trace Species (ACATS-IV)," by J. M. Gilligan, J. W. Elkins, D. W. Fahey, G. S. Dutton, C. M. Volk, T. J. Baring, R. E. Dunn, and R. C. Myers, Atmospheric Effects of Aviation Project Workshop, Virginia Beach, VA, June 26--July 1, 1994. 
"Interference in the Resonance Fluorescence of Two Trapped Atoms," by U. Eichmann, J.C. Bergquist, J.J. Bollinger, J.M. Gilligan, W.M. Itano, J.G. Raizen, and D.J. Wineland, in Proc. 11th Int’l. Conf. On Laser Science, pp. 43-8 (1993). 
"Light scattered from two atoms," by W. M. Itano, U. Eichmann, J. C. Bergquist, J. J. Bollinger, J. M. Gilligan, M. G. Raizen, and D. J. Wineland in Proc. Int'l. Conference on Lasers, 1993, pp. 410-9. 
"Quantum measurements of trapped ions," by W. M. Itano, J. C. Bergquist, J. J. Bollinger, J. M. Gilligan, D. J. Heinzen, F. L. Moore, M. G. Raizen, and D. J. Wineland, Vistas in Astronomy, 37, 169-83 (1993). 
"Ultra-high precision spectroscopy for fundamental physics," by W. M. Itano, J. C. Bergquist, J. J. Bollinger, J. M. Gilligan, D. J. Heinzen, F. L. Moore, M. G. Raizen, and D. J. Wineland, Hyperfine Interactions 78, 211-20 (1993). 
"H2, D2, and HD ionization potentials by accurate calibration of several iodine lines," by D. Shiner, J. M. Gilligan, B. M. Cook, and W. Lichten, Phys. Rev. A 47, 4042-5 (1993). 
"Quantum projection noise: Population fluctuations in two-level systems," by W. M. Itano, J. C. Bergquist, J. J. Bollinger, J. M. Gilligan, F. L. Moore, and M. G. Raizen, Phys. Rev. A 47, 3554-70 (1993). 
"Young's interference experiment with light scattered from two atoms," by U. Eichmann, J. C. Bergquist, J. J. Bollinger, J. M. Gilligan, W. M. Itano, D. J. Wineland, and M. G. Raizen. Phys. Rev. Lett. 70, 2359-62 (1993) 
"Using archie to find files on the internet," J. M. Gilligan, Optics and Photonics News 3 (12), 61 (Dec. 1992). 
"Precise determinations of ionization potentials and EF state energy levels of H2, HD, and D2," by J. M. Gilligan and E. E. Eyler, Phys. Rev. A 46, 3676-90 (1992). 
"Ionic crystals in a linear Paul trap," by M. G. Raizen, J. M. Gilligan, J. C. Bergquist, W. M. Itano, and D. J. Wineland, Phys. Rev. A 45, 6493-501 (1992). 
"Linear trap for high-accuracy spectroscopy of stored ions," by M. G. Raizen, J. M. Gilligan, J. C. Bergquist, W. M. Itano, and D. J. Wineland, J. Mod. Opt. 39, 233-42 (1992). 
"High-resolution three-photon spectroscopy and multiphoton interference in molecular hydrogen," by J. M. Gilligan and E. E. Eyler, Phys. Rev. A 43, 6406-9 (1991). 
"High-resolution spectroscopy of laser-cooled ions", by D. J. Wineland, J. C. Bergquist, J. J. Bollinger, W. M. Itano, F. L. Moore, J. M. Gilligan, M. G. Raizen, D. J. Heinzen, C. S. Weimer, and C. H. Manney, in Proc. Enrico Fermi Summer School on Laser Manipulation of Atoms and Ions, July 1991, Varenna, Italy, pp. 539-51. 
"Recent experiments on trapped ions at the National Institute of Standards and Technology," by D. J. Wineland, J. C. Bergquist, J. J. Bollinger, W. M. Itano, F. L. Moore, J. M. Gilligan, M. G. Raizen, D. J. Heinzen, C. S. Weimer, and C. H. Manney, in Proc. Enrico Fermi Summer School on Laser Manipulation of Atoms and Ions, July 1991, Varenna, Italy, pp. 553-67. 
Precise Multiphoton Spectroscopy of the H2, HD, and D2 Molecules and a New Determination of the Ionization Potential of HD, Ph.D. dissertation, Yale University, 1991. 
"Measurement of high Rydberg states and the ionization potential of H2," by E. McCormack, J. M. Gilligan, C. Cornaggia, and E. E. Eyler, Phys. Rev. A 39, 2260-3 (1989). 
"Precise multiphoton spectroscopy of H2," by E. E. Eyler, J. M. Gilligan, and E. McCormack, in Advances in Laser Spectroscopy III, AIP Conference Proceedings No. 172, pp. 331-3 (1988). 
"Precise two-photon spectroscopy of E¬ X* intervals in H2," by E. E. Eyler, J. M. Gilligan, E. McCormack, A. Nussenzweig, and E. Pollack, Phys. Rev. A 36, 3486-89 (1987). 
"Precise multiphoton spectroscopy of excited states of H2, by E. E. Eyler, J. M. Gilligan, and E. McCormack, in Advances in Laser Spectroscopy II, AIP Conference Proceedings No. 160, pp. 388-90 (1987). 
"Precise photodissociation and multiphoton spectroscopy of H2," by E. McCormack, E. E. Eyler, and J. M. Gilligan, in XV International Conference on Quantum Electronics, Technical Digest Series 1987 (Optical Society of America, Washington, DC, 1987), Vol. 21, pp. 58-60. 
\end{rubric}
