\begin{rubric}{Science Policy Activities}%
\entry*[2008]Co-leader, Faculty Seminar on ``Technology, Commonweal, and the Transformation of Humanity'' Center for Ethics, Vanderbilt University (May 12--15 2008)
\entry*[2008]Session organizer \& chair, ``Quantifying Individual Emissions'' session, Consumption, Law, \& Environment Conference, Vanderbilt Law School (Apr.~17--19 2008).
\entry*[2007--]Associate Director for Research, Vanderbilt Climate Change Research Network, Law School and Owen Graduate School of Management. Research on policy related to greenhouse gas emissions due to individual and household behavior.
\entry*[2006]Discussion Leader, ``Intra- and Inter-Generational Equity'' panel, Consumption, Law, \& Environment Roundtable, Vanderbilt Law School, Oct.~19--20.
\entry*[2005]Co-leader, Faculty seminar on Threats to Environmental Sustainability, Vanderbilt Center for the Study of Religion and Culture.
\entry*[2004--]Fellow, Center for the Study of Religion and Culture and core member, Ecology and Spirituality research group.
\entry*[2003]Participant, Workshop on environmental risks (M. Vandenbergh, Chair).
\entry*[1999--2000]Co-chair (with Lewis Branscomb), faculty seminar on Science and Technology Policy, Vanderbilt University.
\entry*[1996--1997]Chair, faculty seminar on Economics of Scientific Research, Vanderbilt Institute for Public Policy Studies.
\entry*[1996]Pan-American Science, Technology, and Economic Development Project, Vanderbilt University.
\entry*[1996]National Academy of Sciences Convocation on Doctoral Programs in Science and Engineering.
\entry*[1991--1995]Editorial board, Young Scientists' Network.
\entry*[1993]Prepared report for Executive Committee of American Physical Society Division of Atomic, Molecular, and Optical Physics on retention, career advancement, and diversity issues for young physicists.
\end{rubric}
