\item[2024--2027] Steering committee, Community Surface Dynamics Modeling System, an NSF-funded international center for integrated modeling of
the evolution of landscapes and sedimentary basins. My role focuses on guiding
integration of geomorphology modeling with human-systems modeling.
\item[2024--2025] American Geophysical Union Voices for Science. Selected for
  the 2024 cohort on the Science Policy track. Receive training from AGU in
  communicating with policymakers about policy implications of my research and
  conduct monthly public outreach events over the following year.
\item[2023--2025] Advisory Board/Technical Advisory Group,
  Southwest Urban Corridor Integrated Field Laboratory (SW-IFL),
  a collaboration between Arizona State University, University of Arizona,
  Northern Arizona University, Oak Ridge National Laboratory,
  Brookhaven National Laboratory, and IBM.
\item[2021--present] Associate Editor for Climate Law and Policy,
   \emph{Frontiers in Climate}.
\item[2016--2023] Program Committee,
  Environmental and Sustainability Applications track,
  Winter Simulation Conference, IEEE and INFORMS.
\item[2023] Panel and \emph{ad-hoc\/} grant proposal review for National Science Foundation.
\item[2016--2022] Organizing committee,
  Annual Conference on Artificial Intelligence and the Law,
  Vanderbilt Law School.
\item[2016--2021] External Advisory Committee,
  Urban Water Innovation Network, an NSF-sponsored sustainability
  research network (\$12.5 million funding).
\item[2022] Candidate for President of the Global Environmental Change
  section of the American Geophysical Union. Nominated by President-elect
  Andrew Dessler. I was not elected.
\item[2022] Grant proposal review panel, National Science Foundation.
\item[2022] Presubmission ``red-team'' review and feedback on grant proposals,
  by University of Texas, Austin and Colorado State University.
\item[2021] External tenure review for Northeastern University
\item[2021] Grant proposal review for Nederlandse Organisatie voor Wetenschappelijk
  (Dutch Research Council).
\item[2019--2021] Member, External Advisory Committee,
  ``Water Unaffordability in the United States,''
  an NSF-sponsored research project. Laura Senier, PI.
\item[2019] Member, scientific committee,
  First International Conference on Environmental Non-Migration,
  Dresden Germany, June 19--21, 2019.
\item[2019] With Michael Vandenbergh, I co-organized a conference on
  ``The Tenth Anniversary of the Behavioral Wedge'' at Vanderbilt Law School,
   Feb.~29--Mar.~1, 2019.
\item[2018] NSF grant review panel.
\item[2018] Member, Working Group on the Use of Socio-Environmental Systems
  Modeling in Actionable Science,
  National Socio-Environmental Synthesis Center
  (National Science Foundation and University of Maryland).
\item[2018] Co-Chair, Environmental and Sustainability Applications Track,
   Winter Simulation Conference (Gothenburg, Sweden), Dec. 9--12 2018.
   Responsible for working with a European counterpart to develop the ESA
   track, including inviting speakers and session proposals, coordinating
   peer-review of submitted papers, appointing session chairs, and scheduling
   session.
\item[2017--2018] Participant, NSF workshop on
  Interdisciplinary Disaster Research.
  Developing resources on best practices for interdisciplinary disaster
  research.
\item[2017--2018] Member, Human Dimensions Working Group,
  Community Surface Dynamics Modeling System (University of Colorado, Boulder).
\item[2017] Invited reviewer of National Academies report,
  \emph{The Human Element: Integrating Social and Behavioral Sciences in the
    Weather Enterprise}
\item[2017] Founding member and member of launch team,
  The Erd\H{o}s Institute for Collaborative Research, Innovation, and
  Entrepreneurship, Columbus, OH.
  The Erd\H{o}s Institute is an offshoot of a joint effort by Vanderbilt and
  Ohio State to foster innovative collaborative interdisciplinary research by
  faculty, and to stimulate the commercialization of research products through
  partnerships with private industry and sources of early investment funds.
\item[2015] Organizing Committee:
  Food, Energy, Water Systems Nexus Challenges Workshop: Technology and
  Information Fusion (sponsored by NSF, Nov. 5--6, 2015).
\item[2007] Represented Vanderbilt University at Oak Ridge National Laboratory
  University Liaisons Meeting: Opportunities for Collaborative Research on
  Climate Change, Sept 26.
\item[2008] Session organizer and chair, ``Quantifying Individual Emissions,''
  Consumption, Law, \& Environment Conference, Vanderbilt Law School
  (Apr.\ 17--19, 2008).
\item[2006] Chair, ``Intra- and Inter-Generational Equity'' session,
  Consumption, Law, \& Environment Workshop, Vanderbilt Law School
  (Oct.~19--20, 2006).
\item[1997] Chair, Program Session on Laser and Ion-Beam Processing,
  ASM Materials Week '97, In\-di\-an\-a\-po\-lis, IN.
\item[1996] Co-Chair, Program Session on Laser and Ion-Beam Processing,
  ASM Materials Week '96, Cincinnati, OH.
\item[1996] Organizing Committee,
   5$^{\mbox{\scriptsize th}}$ Annual Workshop of the Consortium for
   Nanostructured Materials, Nashville TN.
\item[Ongoing] Review grant proposals for National Science Foundation,
  U.S. Department of Energy,
  Dutch Research Council,
  UK National Environmental Research Council,
  and Indo-US Science \& Technology Forum.
% \item[Ongoing] Review reports for National Academy of Sciences.
\item[Ongoing] Review journal manuscripts for
  Proceedings of the National Academy of Sciences of the United States,
  Nature Climate Change,
  Nature Sustainability,
  Nature Ecology \& Evolution,
  Nature Communications,
  ACM Transactions on Autonomous and Adaptive Systems,
  Computers, Environment, and Urban Systems
  Climatic Change,
  Ecological Economics,
  Energy Policy,
  Energy Economics,
  Energy Research \& Social Science,
  Environmental Modeling \& Software,
  Environmental Science \& Technology,
  Land Use Policy,
  PLOS ONE,
  Royal Society of Chemistry,
  Sociological Forum,
  Sustainability Science,
  International Journal of Biometeorology,
  Proceedings of the National Academy of Sciences of India,
  and
  International Journal of Sustainable Transportation.
\item[Ongoing] Review book proposals and manuscripts for
  Cambridge University Press,
  Columbia University Press,
  Oxford University Press,
  and Princeton University Press.
