\item[2021] Member, University Working Group on Climate, Environment, and Energy
  Futures.
\item[2021] Grand Rounds lecture in Radiology about climate change and the
  Vanderbilt Medical Center. March 29, 2021.
\item[2018--2019] Worked with Blue Sky sustainability initiative as part of
  FutureVU planning process.
\item[2018] Organized panel on ethics in data science for Data Science Visions
  symposium.
\item[2017--present] Management Committee, The Erd\H{o}s Institute for
  Collaborative Research, Innovation, and Entrepreneurship (A joint venture of
  The Ohio State University and Vanderbilt University).
\item[2017] Co-chair (with Gail Carr-Williams), Public Transit Working Group,
  Transportation Planning, Vanderbilt FutureVU land-use planning initiative.
\item[2017] ``Climate Science Myth Busters'' Public lecture on myths and facts
  about climate science and global warming. School of Engineering (Apr.~12).
\item[2017] Led the inaugural Digital Salon at the Wond'ry, discussing
  cross-disciplinary applications of data science and computational modeling
  from engineering and the natural sciences to digital humanities (Feb.~21).
\item[2016] Panelist, ``After Paris, What Next?''  Roundtable discussion of
  climate policy after the Paris accord. Vanderbilt Law School, hosted by
  Chancellor Zeppos.
\item[2015--2017] Working with the Curb Center and the Wond'ry to build
  multi-university consortium to foster interdisciplinary faculty collaboration
  (Vanderbilt and Ohio State, founding members).  Worked with Prof.\ Roman
  Holowinsky at Ohio State to launch the Erd\"os Institute at Ohio State and
  develop university-industry connections to help doctoral students prepare for
  successful non-academic careers in the private sector.
% \item[2015--2017] Worked with the Curb Center and the Wond'ry to build multi-university consortium to foster interdisciplinary faculty collaboration. This work led to the creation of the Erd\H{o}s Institute.
\item[2015] Panelist, ``Grand Challenge: Energy and the Future,'' (Vanderbilt
  Board of Trust Meeting, 13~Feb.)
\item[2013] Panelist, ``Starting the Conversation: Inspiring Your Students to
  Write'' (Aug.~29, Center for Teaching, Writing Studio, \& Heard Library).
\item[2013] Speaker, ``Dinner and a draft: Talking about writing and revising''
  (Mar.~28, Dean of Commons \& Writing Studio).
\item[2013] Graduate honor fellowships evaluation committee.
\item[2010--2013] Traffic \& Parking Committee.
\item[2008] Co-chair (with Michael Bess), Faculty Seminar on the Future of
  Humanity, Center for Ethics.
\item[1999--2000] Co-chair (with Lewis Branscomb) Faculty Seminar on Science
  and Technology Policy.
\item[1996--1997] Chair, Faculty Seminar on Economics of Scientific Research
  (Vanderbilt Institute for Public Policy Studies).
\item[Ongoing] Frequent guest lectures about climate change and science policy
  in Nursing, Global Public Health, Law, Management, Engineering, and Arts \&
  Science; speaking to student groups, such as Students Promoting Environmental
  Awareness and Responsibility, Wilderness Skills, McGill Hour, and Commons.
