\item[2021--present] Co-chair, Climate Studies Program Committee.
  Developed a new interdisciplinary major in Climate Studies, which was adopted by the 
  College of Arts and Science.
\item[2022--2023] College Working Group on the Future of the
  Undergraduate Curriculum,
  developed a new curriculum structure for College of Arts \& Science.
  The new curriculum introduces a novel interdisciplinary core to provide undergraduates with a shared experience, introduces them to the purpose and value of a liberal arts education, and reduces the burden of general education distribution requirements, to make it more straightforward for students to navigate the new curriculum.
  College faculty approved the new curriculum 70\% to 30\%.
\item[2020--2023] Director, Vanderbilt Climate and Society Grand Challenge
  Initiative. Lead an interdisciplinary project to build strong ties among
  Humanities, Social Sciences, and Natural Sciences in research and teaching on
  the nexus of climate change and society.
\item[2020--2022] Junior Advisory Review Committee (JARC).
  Conduct third-year reviews for tenure-track faculty.
\item[2022] Presentation to Arts \& Science Board of Advisors about the new
  Climate Studies major and the Climate \& Society Grand Challenge Initiative.
  Mar.~25.
\item[2022] Keynote talk for Communication of Science, Engineering, and
  Technology Symposium (sponsored by National Endowment for Humanities grant).
  Mar.~18.
\item[2021--2022] Faculty Search Committee, Environmental Religious Studies.
\item[2019--2020] Arts \& Science Grand Challenges Committee.
  Evaluated proposals to the college's Grand Challenges Initiative for
  interdisciplinary projects to address the most pressing problems facing
  society.
\item[2019--2020] Faculty Search Committee: Environmental Asian Studies, Asian Studies program.
\item[2003--2018] Communication of Science, Engineering, and Technology Committee.
\item[2014--2015] Worked with Prof.\ Tiffiny Tung (Anthropology) on addressing problems of sexual harassment and hostile work environments for students conducting field research. Sought guidance from EEO and developed recommendations that Prof.\ Tung presented to Faculty Council.
\item[2004--2009] Writing Advisory Board.
