\item Julia Tilton (2021--2022, EES major): Supervised research on developing
a composite index of climate change.
\item Ao Qu (2020--21, Computer science major): Supervised research on applying
machine learning to analyzing agent-based model simulations. Mr. Qu co-authored
a peer-reviewed paper based on his research.
\item Ellie Miller (2021, EES major): Supervised research on extreme heat and
humidity in climate model simulations.
\item Robin Young (2021--22, EES major): Supervised research on extreme heat
and humidity in historical records and climate model simulations, which are
part of his immersion project.
\item Margaret Dorhout (2018--2020, EES major): Supervised research on extreme weather patterns in Bangladesh.
\item Asaf Roth (2019, computer science major): Supervised research on time-series analysis of electricity consumption by buildings on Vanderbilt campus.
\item Madeline Allen (2018--2019, EES major): Supervised senior honors thesis research on flood modeling (in collaboration with Professors Mark Abkowitz and Janey Camp in Civil \& Environmental Engineering).
\item Emma Rimmer (2018--2019, Environmental Sociology major, EES minor): Supervised research on household energy efficiency in the United States.
\item Umang Chaudhry (2017--2019, EES and Science Communications double-major): Supervised independent research project during academic year, summer research project, and senior honors thesis research on impacts of gentrification on activities of daily life
for public-transit users in the Nashville Metropolitan Statistical Area.
\item Miguel Moravec (2017--2018, EES and CSET double-major): Supervised summer research and supervising senior honors thesis research on the impacts of gentrification on mobility among low-income resildents of the Nashville Metropolitan Statistical Area.
\item Marc Chen (2016--2017, Economics major): Co-supervised senior honors thesis research on poverty, access to public-transit, and employment in Nashville, and served as second reader of honors thesis. Mr. Chen's thesis was awarded highest honors.
\item Austin Channell (2015--2017, Civil Engineering major): Supervised immersive undergraduate research project on reducing individual and household greenhouse gas emissions.
Mr.~Channell won a Vanderbilt Undergraduate Summer Research fellowship to support this work and won a prize for his presentation of this work at the 2016 Vanderbilt Undergraduate Research Fair.
\item Heebong Kim (2016, EES major): Supervised honors enrichment project on science policy.
\item Joshua Timm (2015--2016, Political Science major): Supervised independent research on media bias in reporting on climate and weather and immersive research on corporate energy conservation as part of a TIPs project. Second reader on senior honors thesis.
\item Michael Diamond (2014, EES major): Supervised field research in Bangladesh.
\item Michael Diamond (2012, EES major): Supervised independent honors research project on the feasibility of terraforming Mars.
\item Michael Kofsky (2010--11, Political Science major): Supervised independent research on the environmental footprints of delivering movies for home viewing by mailing DVD's versus streaming broadband.
\item Jeremy Doochin (2008--09, Independent major in Environmental Policy): Supervised independent research project on corporate greenhouse gas emissions reduction.
\item Kelley Coffman (2004--05, Medicine, Health, \& Society major): Supervised senior honors thesis on citizen response to environmental contamination by Oak Ridge National Laboratory. Ms. Coffman received high honors for her thesis.
\item Megan O'Grady (2002--03, Physics major): Co-supervised senior research project and honors thesis together with Prof.~John Wikswo. Ms.~O'Grady subsequently won an NSF Graduate Fellowship.
